---
title: "Perceptions of urban environment DataSchema"
output: html_document
---
# Table of Contents
1. [General neighborhood safety subdomain](#general-neighborhood-safety-subdomain)
2. [Social trust subdomain](#social-trust-subdomain)
3. [Vandalism subdomain](#vandalism-subdomain)
4. [Social cohesion subdomain](#social-cohesion-subdomain)

# General neighborhood safety subdomain

### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsafe_0   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   Feels safe at night  
0 |   Does not feel safe at night  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsafe_1   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   Feels safe at night  
0 |   Does not feel safe at night 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsafe_2   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   Feels safe at night  
0 |   Does not feel safe at night 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsafe_3   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   Feels safe at night  
0 |   Does not feel safe at night 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsafe_4   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   Feels safe at night  
0 |   Does not feel safe at night 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsafe_5   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   Feels safe at night  
0 |   Does not feel safe at night 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsafe_6   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   Feels safe at night  
0 |   Does not feel safe at night  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe in the neighbourhood     
**Variable name**: env_nbh_sf_0   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood.   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   Feels safe 
0 |   Does not feel safe  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe in the neighbourhood     
**Variable name**: env_nbh_sf_2   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood.   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   Feels safe 
0 |   Does not feel safe   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Social trust subdomain

### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_0   
**Variable description**:  Indicator of whether the participant is asked if most people in the area where they live  (i.e. in their neighbourhood)  can be trusted.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | People can be trusted    
0 | People cannot be trusted         

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_1   
**Variable description**:  Indicator of whether the participant is asked if most people in the area where they live  (i.e. in their neighbourhood)  can be trusted.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | People can be trusted    
0 | People cannot be trusted       

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_2     
**Variable description**:  Indicator of whether the participant is asked if most people in the area where they live  (i.e. in their neighbourhood)  can be trusted.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | People can be trusted    
0 | People cannot be trusted      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_4     
**Variable description**:  Indicator of whether the participant is asked if most people in the area where they live  (i.e. in their neighbourhood)  can be trusted.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | People can be trusted    
0 | People cannot be trusted       

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```


# Vandalism subdomain

### **Variable label**: Neighbourhood cleanliness   
**Variable name**:  env_nbh_clean_0  
**Variable description**:  Indicator of whether the participant perception of the cleanliness (presence of rubbish) of the area where respondent lives (i.e. their neighbourhood).  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Not very clean     
2 | Not clean   
3 | Mostly clean   
4 | Clean             

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood graffiti and vandalism  
**Variable name**:  env_nbh_grfvnd_0  
**Variable description**:  Indicator of whether the participant perception of the cleanliness (presence of rubbish) of the area where respondent lives (i.e. their neighbourhood).  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | A lot of graffiti and vandalism      
2 | Some graffiti and vandalism     
3 | A little graffiti and vandalism     
4 | No graffiti and vandalism              

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood noise    
**Variable name**:  env_nbh_noise_0  
**Variable description**:  Indicator of whether the participant’s perception of presence of excessive noise in their neighbourhood.     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Definitely excessive noise      
2 | Some excessive noise    
3 | A little excessive noise    
4 | No excessive noise            

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood noise    
**Variable name**:  env_nbh_noise_1  
**Variable description**:  Indicator of whether the participant’s perception of presence of excessive noise in their neighbourhood.     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Definitely excessive noise      
2 | Some excessive noise    
3 | A little excessive noise    
4 | No excessive noise            

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
# Social cohesion subdomain

### **Variable label**: Helpful neighbours  
**Variable name**: env_nbs_help_0  
**Variable description**: Indicator of whether the participant agrees that neighbors would help them if needed, in case of emergency/trouble.  
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Neighbours would help me   
0 | Neighbours would not help me       

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Helpful neighbours  
**Variable name**: env_nbs_help_2  
**Variable description**: Indicator of whether the participant agrees that neighbors would help them if needed,  in case of emergency/trouble.  
**Value type**: integer   
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Neighbours would help me    
0 | Neighbours would not help me         

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Helpful neighbours  
**Variable name**: env_nbs_help_4  
**Variable description**: Indicator of whether the participant agrees that neighbors would help them if needed,  in case of emergency/trouble.  
**Value type**: integer   
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Neighbours would help me   
0 | Neighbours would not help me      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Neighbours cooperate  
**Variable name**: env_nbs_coop_0   
**Variable description**: Indicator of whether the participant agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out.  
**Value type**: integer  
**Variable unit**: N/A   
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | People willing to help each other   
0 | People not willing to help each other         

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Neighbours cooperate    
**Variable name**: env_nbs_coop_1  
**Variable description**: Indicator of whether the participant agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out.    
**Value type**: integer    
**Variable unit**: N/A     
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | People willing to help each other   
0 | People not willing to help each other             

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Neighbours cooperate    
**Variable name**: env_nbs_coop_2  
**Variable description**: Indicator of whether the participant agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out.    
**Value type**: integer    
**Variable unit**: N/A     
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | People willing to help each other   
0 | People not willing to help each other               

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbours cooperate    
**Variable name**: env_nbs_coop_3  
**Variable description**: Indicator of whether the participant agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out.    
**Value type**: integer    
**Variable unit**: N/A     
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | People willing to help each other   
0 | People not willing to help each other            

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Neighbours cooperate    
**Variable name**: env_nbs_coop_4  
**Variable description**: Indicator of whether the participant agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out.    
**Value type**: integer    
**Variable unit**: N/A     
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | People willing to help each other   
0 | People not willing to help each other             

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Neighbourhood values and norms       
**Variable name**: env_nbh_values_0   
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood share similar values and norms.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people share similar values and norms    
2 | Agree that people share similar values and norms
3 | Neither agree or disagree that people share similar values and norms
4 | Disagree that people share similar values and norms  
5 | Strongly disagree that people share similar values and norms        

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Neighbourhood values and norms       
**Variable name**: env_nbh_values_2     
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood share similar values and norms.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people share similar values and norms   
2 | Agree that people share similar values and norms
3 | Neither agree or disagree that people share similar values and norms  
4 | Disagree that people share similar values and norms  
5 | Strongly disagree that people share similar values and norms       

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood values and norms       
**Variable name**: env_nbh_values_4     
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood share similar values and norms.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people share similar values and norms   
2 | Agree that people share similar values and norms
3 | Neither agree or disagree that people share similar values and norms 
4 | Disagree that people share similar values and norms  
5 | Strongly disagree that people share similar values and norms       

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_0   
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood  get along with each other.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people get along  
2 | Agree that people get along  
3 | Neither agree or disagree that people get along   
4 | Disagree that people get along    
5 | Strongly disagree that people get along        

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_2   
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood  get along with each other.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people get along      
2 | Agree that people get along  
3 | Neither agree or disagree that people get along   
4 | Disagree that people get along     
5 | Strongly disagree that people get along         

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_3   
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood  get along with each other.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people get along     
2 | Agree that people get along  
3 | Neither agree or disagree that people get along    
4 | Disagree that people get along    
5 | Strongly disagree that people get along        

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_4   
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood  get along with each other.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people get along     
2 | Agree that people get along  
3 | Neither agree or disagree that people get along   
4 | Disagree that people get along    
5 | Strongly disagree that people get along         

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbours are friendly       
**Variable name**: env_nbs_friend_0     
**Variable description**: Indicator of whether the participant is asked whether members of the area where their live (i.e. their neighbourhood) are friendly/ polite.           
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | People are friendly    
2 | People are somewhat friendly 
3 | People are not really friendly  
4 | People are not friendly    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Belonging to neighbourhood        
**Variable name**: env_nbh_belong_0      
**Variable description**: Indicator of whether the participant asked whether they feel a part of the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Feel     
0 | No   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Belonging to neighbourhood        
**Variable name**: env_nbh_belong_2      
**Variable description**: Indicator of whether the participant asked whether they feel a part of the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Yes    
0 | No     

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Belonging to neighbourhood        
**Variable name**: env_nbh_belong_4      
**Variable description**: Indicator of whether the participant asked whether they feel a part of the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Yes    
0 | No    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_0      
**Variable description**: Indicator of whether the participant agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree    
2 | Agree 
3 | Neither agree or disagree  
4 | Disagree   
5 | Strongly disagree          

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_2      
**Variable description**: Indicator of whether the participant agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree    
2 | Agree 
3 | Neither agree or disagree  
4 | Disagree   
5 | Strongly disagree         

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_3      
**Variable description**: Indicator of whether the participant agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree    
2 | Agree 
3 | Neither agree or disagree  
4 | Disagree   
5 | Strongly disagree         

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_4      
**Variable description**: Indicator of whether the participant agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree    
2 | Agree 
3 | Neither agree or disagree  
4 | Disagree   
5 | Strongly disagree          

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Sense of community        
**Variable name**: env_nbh_comm_0      
**Variable description**: Members of community in which participant lives has a sense of community and collective identity.     
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Good sense of collective identity and community in the neighbourhood   
2 | Some sense of collective identity and community in the neighbourhood 
3 | Not really a sense of collective identity and community in the neighbourhood  
4 | No sense of collective identity and community at all in the neighbourhood  
5 | Don't know if sense of collective identity and community neighbourhood          

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
