---
title: "Perceptions of urban environment DataSchema"
output: html_document
---
# Connecting with Opal data server
## Login to server and assign study data
```{r, echo=FALSE}
#Load R libraries
library(opal)
library(tidyverse)
library(epiDisplay)
# Create an opal object with the login information
erasmus_opal <- opal.login()
## When you are done with your work, logout of Opal server
opal.logout(erasmus_opal) 
# Login to Opal server and assign the content of the RECORD table(s) to your RStudio environment

# Record wave 1 part 1
opal.assign.table.tibble(erasmus_opal, 'RECORD_w1_1','RECORD.RECORD_w1_1', variables=list('Q6_b_1','Q6_b_2','Q6_b_3','Q6_b_4','Q8_1_a','Q8_1_b','Q8_1_c','Q8_1_d')) 
RECORD_w1_1 <- opal.execute(erasmus_opal,'RECORD_w1_1')

# RECORD wave 1 part 2
opal.assign.table.tibble(erasmus_opal, 'RECORD_w1_2', 'RECORD.RECORD_w1_2',variables=list('q12_no_securite','q6_no_confianc','q6_no_voisserv','q10_no_pbordure','q10_no_vandalis','q10_no_bruitgen','q16_no_aidetach','q11_no_aimables','q8_no_inidcoll','q11_no_habsoude','q10_no_incivili','q22_no_reconfor'))
RECORD_w1_2 <- opal.execute(erasmus_opal,'RECORD_w1_2')
#RECORD_w1_2$

# RECORD wave 2
opal.assign.table.tibble(erasmus_opal, 'RECORD_w2', 'RECORD.RECORD_W2', variables=list('P45_Q1_994','P45_Q1_995','P45_Q1_996','P45_Q1_997','P43_Q5_960','P43_Q5_961','P43_Q5_962','P43_Q5_963','P44_Q2_972','P44_Q2_973','P44_Q2_974','P44_Q2_975','P46_Q1_1016','P46_Q1_1017','P43_Q2_945','P43_Q2_946','P43_Q2_947','P43_Q2_948','P40_Q2_881','P40_Q2_882','P40_Q2_883','P40_Q2_885','P48_Q2_1060','P48_Q2_1061','P48_Q2_1062','P48_Q2_1063','P46_Q5_1028','P46_Q5_1029','P46_Q6_1030','P46_Q6_1031','P44_Q5_987','P44_Q5_988','P44_Q5_989','P44_Q5_990','P46_Q3_1022','P46_Q3_1023','P43_Q1_940','P43_Q1_941','P43_Q1_942','P43_Q1_943','P48_Q3_1065','P48_Q3_1066','P48_Q3_1067','P48_Q3_1068','P46_Q4_1024','P46_Q4_1025','P47_Q3_1049','P47_Q3_1050','P47_Q3_1051','P47_Q3_1052'))  
RECORD_w2 <- opal.execute(erasmus_opal,'RECORD_w2')
#RECORD_w2$
```
## Assign participant id as first column of your harmonized dataframes
```{r,echo=FALSE}
env_RECORD_0 <- data.frame(id = RECORD_w1_1$id)
env_RECORD_1 <- data.frame(id = RECORD_w2$id)
```
# Table of Contents

1. [General neighbourhood safety subdomain](#general-neighbourhood-safety-subdomain)
2. [Social trust subdomain](#social-trust-subdomain)
3. [Social cohesion subdomain](#social-cohesion-subdomain)  
4. [Neighbourhood aesthetics subdomain](#vandalism-subdomain)
5. [Crime and vandalism subdomain](#crime-and-vandalism-subdomain)  

# General neighbourhood safety subdomain

### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsf_0   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------   
0 |   Does not feel safe at night
1 |   Feels safe at night 

**Harmonization status**:  complete 
**Harmonization comment**:   RECORD item does not ask about night safety in particular but item is comparable to being asked about night safety per B.Chaix. 'Always feels safe' and 'mostly feels safe' have been recoded as 'feels safe'.
**R script**:  
```{r, echo=TRUE}
table(RECORD_w1_2$q12_no_securite)
summary(RECORD_w1_2$q12_no_securite)
#not an integer
#1 and 2 = no not safe,  3 and 4=yes safe 
env_RECORD_0$env_nbh_nsf_0 <-recode(as.integer(RECORD_w1_2$q12_no_securite),'1'=0L,'2'=0L,'3'=1L,'4'=1L)
table(env_RECORD_0$env_nbh_nsf_0)

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsf_1   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------   
0 |   Does not feel safe at night 
1 |   Feels safe at night 

**Harmonization status**:   complete
**Harmonization comment**: RECORD item does not ask about night safety in particular but item is comparable to being asked about night safety per B.Chaix. 'Always feels safe' and 'mostly feels safe' have been recoded as 'feels safe'.
**R script**:  
```{r, echo=TRUE}
table(RECORD_w2$P45_Q1_994) #1= safe
table(RECORD_w2$P45_Q1_995)  #1= safe 
table(RECORD_w2$P45_Q1_996)  #1= not 88
table(RECORD_w2$P45_Q1_997)   #1= not  477  
summary(RECORD_w2$P45_Q1_997)
typeof(RECORD_w2$P45_Q1_997)
#not an integer, recode as an integer 

env_RECORD_1$env_nbh_nsf_1 <- as.integer(ifelse((RECORD_w2$P45_Q1_994 == '1' | RECORD_w2$P45_Q1_995 == '1'), 1,                                               (ifelse (RECORD_w2$P45_Q1_996 == '1' | RECORD_w2$P45_Q1_997 == '1', 0, NA))))
table(env_RECORD_1$env_nbh_nsf_1)

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsf_2   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------   
0 |   Does not feel safe at night 
1 |   Feels safe at night 

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsf_3   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe at night 
1 |   Feels safe at night  


**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsf_4   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe at night 
1 |   Feels safe at night  


**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsf_5   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe at night
1 |   Feels safe at night  
 

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsf_6   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe at night
1 |   Feels safe at night  
  

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_0   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood.        
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe 
1 |   Feels safe 
 

**Harmonization status**:   complete
**Harmonization comment**:  'Always feels safe' and 'mostly feels safe' have been recoded as 'feels safe'. 
**R script**:  
```{r, echo=TRUE}
table(RECORD_w1_2$q12_no_securite)
summary(RECORD_w1_2$q12_no_securite)
#not an integer
#1 and 2 = no not safe,  3 and 4=yes safe 
env_RECORD_0$env_nbh_sf_0 <-recode(as.integer(RECORD_w1_2$q12_no_securite),'1'=0L,'2'=0L,'3'=1L,'4'=1L)
table(env_RECORD_0$env_nbh_sf_0)

```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_1   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood.     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe
1 |   Feels safe 
  

**Harmonization status**:   complete
**Harmonization comment**:   'Always feels safe' and 'mostly feels safe' have been recoded as 'feels safe'.
**R script**:  
```{r, echo=TRUE}
table(RECORD_w2$P45_Q1_994) #1= safe
table(RECORD_w2$P45_Q1_995)  #1= safe 
table(RECORD_w2$P45_Q1_996)  #1= not 88
table(RECORD_w2$P45_Q1_997)   #1= not  477  
summary(RECORD_w2$P45_Q1_997)
typeof(RECORD_w2$P45_Q1_997)
#not an integer, recode as an integer 

env_RECORD_1$env_nbh_sf_1 <- as.integer(ifelse((RECORD_w2$P45_Q1_994 == '1' | RECORD_w2$P45_Q1_995 == '1'), 1,                                               (ifelse (RECORD_w2$P45_Q1_996 == '1' | RECORD_w2$P45_Q1_997 == '1', 0, NA))))
table(env_RECORD_1$env_nbh_sf_1)

```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_2   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood.       
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe 
1 |   Feels safe 
  

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_3   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood.       
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe  
1 |   Feels safe 
 

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_4   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe  
1 |   Feels safe 
 

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_5   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood.       
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe  
1 |   Feels safe 
 

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_6   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood.      
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe 
1 |   Feels safe 
  

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
# Social trust subdomain

### **Variable label**:  Trust in neighbours     
**Variable name**:  env_nbh_trust_0   
**Variable description**:  Indicator of whether the participant agrees that most people in the area where they live (i.e. in their neighbourhood) can be trusted.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People cannot be trusted 
1 | People can be trusted    
        

**Harmonization status**:   complete
**Harmonization comment**:   RECORD asks if respondent trusts neighbours with belongings. 
**R script**:  
```{r, echo=TRUE}
table(RECORD_w1_2$q6_no_confianc)
summary(RECORD_w1_2$q6_no_confianc)
#not an integer
#1 and 2 = agree, trust ,  3 and 4=disagree
env_RECORD_0$env_nbh_trust_0 <-recode(as.integer(RECORD_w1_2$q6_no_confianc),'1'=1L,'2'=1L,'3'=0L,'4'=0L)
table(env_RECORD_0$env_nbh_trust_0)

```
### **Variable label**:  Trust in neighbours  
**Variable name**:  env_nbh_trust_1   
**Variable description**:  Indicator of whether the participant agrees that most people in the area where they live (i.e. in their neighbourhood) can be trusted.     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People cannot be trusted
1 | People can be trusted    
       

**Harmonization status**:   impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**:  Trust in neighbours  
**Variable name**:  env_nbh_trust_2     
**Variable description**:  Indicator of whether the participant agrees that most people in the area where they live (i.e. in their neighbourhood) can be trusted.     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People cannot be trusted  
1 | People can be trusted    
    

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**:  Trust in neighbours    
**Variable name**:  env_nbh_trust_3     
**Variable description**:  Indicator of whether the participant agrees that most people in the area where they live (i.e. in their neighbourhood) can be trusted.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People cannot be trusted   
1 | People can be trusted    
   

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**:  Trust in neighbours  
**Variable name**:  env_nbh_trust_4     
**Variable description**:  Indicator of whether the participant agrees that most people in the area where they live (i.e. in their neighbourhood) can be trusted.     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People cannot be trusted 
1 | People can be trusted    
      

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_among_0   
**Variable description**:  Indicator of whether the participant agrees that there is trust among the people in the area where they live (i.e. in their neighbourhood).    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
------------- | -------------  
0 | People do not trust one another 
1 | People trust one another  


**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**: 
```{r, echo=TRUE}


```
### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_among_1   
**Variable description**:  Indicator of whether the participant agrees that there is trust among the people in the area where they live (i.e. in their neighbourhood).    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
------------- | -------------  
0 | People do not trust one another 
1 | People trust one another 


**Harmonization status**:   complete   
**Harmonization comment**:  RECORD item asks about distrust among residents as opposed to trust, use with caution. If possible check association of original RECORD item with outcome of interest.   
**R script**: 
```{r, echo=TRUE}

table(RECORD_w2$P48_Q3_1065) # 1= yes, neighbourhood residents definitely distrust each other #2 = other answer
table(RECORD_w2$P48_Q3_1066) # 1= yes, neighbourhood residents somewhat distrust each other #2 = other answer 
table(RECORD_w2$P48_Q3_1067) # 1= yes, neighbourhood residents don't really distrust each other #2 = other answer => trust
table(RECORD_w2$P48_Q3_1068) # 1= yes, neighbourhood residents don't distrust each other at all #2 = other answer  => trust

summary(RECORD_w2$P48_Q3_1065)
#not an integer

env_RECORD_1$env_nbh_trust_among_1 <- as.integer(ifelse((RECORD_w2$P48_Q3_1067 == '1' | RECORD_w2$P48_Q3_1068 == '1'), 1,                                               (ifelse (RECORD_w2$P48_Q3_1065 == '1' | RECORD_w2$P48_Q3_1066 == '1', 0, NA))))

table(env_RECORD_1$env_nbh_trust_among_1)

```
# Social cohesion subdomain

### **Variable label**: Helpful neighbours  
**Variable name**: env_nbs_help_0  
**Variable description**: Indicator of whether the participant agrees that neighbors would help them if needed, in case of emergency/trouble.  
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Neighbours would not help me
1 | Neighbours would help me   
       

**Harmonization status**:   complete
**Harmonization comment**:  2 RECORD items used in harmonization 1. asks if neighbours would help with chores if sick and 2. asks if neighbours could help if sad or depressed.  
**R script**:  
```{r, echo=TRUE}
table(RECORD_w1_2$q16_no_aidetach) #not an integer #1 and 2 = yes help, trust ,  3 and 4=no
summary(RECORD_w1_2$q16_no_aidetach)
table(RECORD_w1_2$q22_no_reconfor) #not an integer #1 and 2 = yes could help   3 and 4=no
summary(RECORD_w1_2$q22_no_reconfor)

env_RECORD_0$env_nbs_help_0 <- as.integer(ifelse((RECORD_w1_2$q16_no_aidetach == '1' | RECORD_w1_2$q16_no_aidetach == '2' | RECORD_w1_2$q22_no_reconfor == '1' | RECORD_w1_2$q22_no_reconfor == '2'), 1,                                              
                                                 (ifelse (RECORD_w1_2$q16_no_aidetach == '3' | RECORD_w1_2$q16_no_aidetach == '4' | RECORD_w1_2$q22_no_reconfor == '3' | RECORD_w1_2$q22_no_reconfor == '4', 0, NA))))
table(env_RECORD_0$env_nbs_help_0)
```
### **Variable label**: Helpful neighbours  
**Variable name**: env_nbs_help_1  
**Variable description**: Indicator of whether the participant agrees that neighbors would help them if needed,  in case of emergency/trouble.  
**Value type**: integer   
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Neighbours would not help me  
1 | Neighbours would help me    
       

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Helpful neighbours  
**Variable name**: env_nbs_help_2  
**Variable description**: Indicator of whether the participant agrees that neighbors would help them if needed,  in case of emergency/trouble.  
**Value type**: integer   
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Neighbours would not help me
1 | Neighbours would help me    
         

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Helpful neighbours  
**Variable name**: env_nbs_help_3    
**Variable description**: Indicator of whether the participant agrees that neighbors would help them if needed,  in case of emergency/trouble.  
**Value type**: integer   
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Neighbours would not help me 
1 | Neighbours would help me    
        

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Helpful neighbours  
**Variable name**: env_nbs_help_4  
**Variable description**: Indicator of whether the participant agrees that neighbors would help them if needed,  in case of emergency/trouble.  
**Value type**: integer   
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Neighbours would not help me  
1 | Neighbours would help me   
    

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```

### **Variable label**: Cooperating neighbours  
**Variable name**: env_nbs_coop_0   
**Variable description**: Indicator of whether the participant agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out.  
**Value type**: integer  
**Variable unit**: N/A   
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People not willing to help each other  
1 | People willing to help each other   
       

**Harmonization status**:   complete 
**Harmonization comment**:  2 RECORD items used in harmonization 1. asks if neighbours help each other and 2. asks if neighbours support each other. For the next wave, DataSchema env_nbs_coop_1, a different item is used. 
**R script**:  
```{r, echo=TRUE}
table(RECORD_w1_1$Q6_b_1)  #Neighbours definitely help each other
table(RECORD_w1_1$Q6_b_2)  #Neighbours help each other
table(RECORD_w1_1$Q6_b_3)  # not
table(RECORD_w1_1$Q6_b_4)  # not 
table(RECORD_w1_2$q6_no_voisserv) # 1 strongly agree that Neighbours support each other # 4= strongly disagree


env_RECORD_0$env_nbs_coop_0  <- as.integer(ifelse((RECORD_w1_1$Q6_b_1 == '1' | RECORD_w1_1$Q6_b_2 == '1'|RECORD_w1_2$q6_no_voisserv == '1' |   RECORD_w1_2$q6_no_voisserv == '2'), 1,                                               
                                  (ifelse (RECORD_w1_1$Q6_b_3 == '1' | RECORD_w1_1$Q6_b_4 == '1' | RECORD_w1_2$q6_no_voisserv == '3' |   RECORD_w1_2$q6_no_voisserv == '4',0, NA))))

table(env_RECORD_0$env_nbs_coop_0)

```

### **Variable label**: Cooperating neighbours    
**Variable name**: env_nbs_coop_1  
**Variable description**: Indicator of whether the participant agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out.    
**Value type**: integer    
**Variable unit**: N/A     
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People not willing to help each other
1 | People willing to help each other   
             

**Harmonization status**:   complete 
**Harmonization comment**:  The RECORD item used asks "Do residents of your neighbourhood work together to solve problems in the neighbourhood?" and therefore differs slightly from the items used to develop env_nbs_coop_0 (which ask if neighbours help or support each other.)    
**R script**:  
```{r, echo=TRUE}
table(RECORD_w2$P47_Q3_1049)  #1 =  neighbours definitely work together to solve problems 
table(RECORD_w2$P47_Q3_1050)   
table(RECORD_w2$P47_Q3_1051)  #1 = Neighbours don't really work together to solve problems
table(RECORD_w2$P47_Q3_1052)   


env_RECORD_1$env_nbs_coop_1  <- as.integer(ifelse((RECORD_w2$P47_Q3_1049 == '1' | RECORD_w2$P47_Q3_1050 == '1'), 1,                                               
                                  (ifelse (RECORD_w2$P47_Q3_1051 == '1' | RECORD_w2$P47_Q3_1052 == '1' ,0, NA))))

table(env_RECORD_1$env_nbs_coop_1)

```

### **Variable label**: Cooperating neighbours      
**Variable name**: env_nbs_coop_2  
**Variable description**: Indicator of whether the participant agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out.    
**Value type**: integer    
**Variable unit**: N/A     
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People not willing to help each other  
1 | People willing to help each other   
             

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Cooperating neighbours      
**Variable name**: env_nbs_coop_3  
**Variable description**: Indicator of whether the participant agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out.    
**Value type**: integer    
**Variable unit**: N/A     
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People not willing to help each other  
1 | People willing to help each other   
          

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Cooperating neighbours      
**Variable name**: env_nbs_coop_4  
**Variable description**: Indicator of whether the participant agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out.    
**Value type**: integer    
**Variable unit**: N/A     
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People not willing to help each other 
1 | People willing to help each other   
            

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  

### **Variable label**: Neighbourhood values and norms       
**Variable name**: env_nbh_values_0   
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood share similar values and norms.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people share similar values and norms    
2 | Agree that people share similar values and norms
3 | Neither agree or disagree that people share similar values and norms
4 | Disagree that people share similar values and norms  
5 | Strongly disagree that people share similar values and norms        

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbourhood values and norms       
**Variable name**: env_nbh_values_1     
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood share similar values and norms.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people share similar values and norms    
2 | Agree that people share similar values and norms
3 | Neither agree or disagree that people share similar values and norms
4 | Disagree that people share similar values and norms  
5 | Strongly disagree that people share similar values and norms        

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbourhood values and norms       
**Variable name**: env_nbh_values_2     
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood share similar values and norms.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people share similar values and norms   
2 | Agree that people share similar values and norms
3 | Neither agree or disagree that people share similar values and norms  
4 | Disagree that people share similar values and norms  
5 | Strongly disagree that people share similar values and norms       

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbourhood values and norms       
**Variable name**: env_nbh_values_3     
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood share similar values and norms.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people share similar values and norms   
2 | Agree that people share similar values and norms
3 | Neither agree or disagree that people share similar values and norms  
4 | Disagree that people share similar values and norms  
5 | Strongly disagree that people share similar values and norms       

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbourhood values and norms       
**Variable name**: env_nbh_values_4     
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood share similar values and norms.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people share similar values and norms   
2 | Agree that people share similar values and norms
3 | Neither agree or disagree that people share similar values and norms 
4 | Disagree that people share similar values and norms  
5 | Strongly disagree that people share similar values and norms       

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_0   
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood  get along with each other.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people get along  
2 | Agree that people get along  
3 | Neither agree or disagree that people get along   
4 | Disagree that people get along    
5 | Strongly disagree that people get along        

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```

### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_1   
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood  get along with each other.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people get along  
2 | Agree that people get along  
3 | Neither agree or disagree that people get along   
4 | Disagree that people get along    
5 | Strongly disagree that people get along        

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```


### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_2   
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood  get along with each other.   
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people get along      
2 | Agree that people get along  
3 | Neither agree or disagree that people get along   
4 | Disagree that people get along     
5 | Strongly disagree that people get along         

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_3   
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood  get along with each other.  
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people get along     
2 | Agree that people get along  
3 | Neither agree or disagree that people get along    
4 | Disagree that people get along    
5 | Strongly disagree that people get along        

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_4   
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood  get along with each other.  
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people get along     
2 | Agree that people get along  
3 | Neither agree or disagree that people get along   
4 | Disagree that people get along    
5 | Strongly disagree that people get along         

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Friendly neighbours       
**Variable name**: env_nbs_friendly_0     
**Variable description**: Indicator of whether the participant is asked whether members of the area where their live (i.e. their neighbourhood) are friendly/ polite.           
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | People are friendly    
2 | People are somewhat friendly 
3 | People are not really friendly  
4 | People are not friendly    

**Harmonization status**:   complete 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(RECORD_w1_2$q11_no_aimables)
summary(RECORD_w1_2$q11_no_aimables)
#not an integer
#1 strongly agree polite neighbours etc.....
env_RECORD_0$env_nbs_friendly_0 <-recode(as.integer(RECORD_w1_2$q11_no_aimables),'1'=1L,'2'=2L,'3'=3L,'4'=4L)
table(env_RECORD_0$env_nbs_friendly_0)

```
### **Variable label**: Belonging to neighbourhood        
**Variable name**: env_nbh_belong_0        
**Variable description**: Indicator of whether the participant asked whether they feel a part of the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not feel part of area
1 | Feels part of area     
   

**Harmonization status**:   complete 
**Harmonization comment**:  Caution, the RECORD item used is only asked of a subset of the sample: the respondents that said yes to the RECORD item preceding this one, which asks respondent if they agree that there is collective efficacy in their neighbourhood. Respondent that did not indicate that they feel that there is collective efficacy in their neighbourhood were not asked if they feel part of the area where they live. 
**R script**:  
```{r, echo=TRUE}

table(RECORD_w1_2$q8_no_inidcoll) 
table(RECORD_w1_1$Q8_1_a) 
summary(RECORD_w1_2$q8_no_inidcoll) # 1 = yes feels part of the community ...4 does not 

env_RECORD_0$env_nbh_belong_0 <-recode(as.integer(RECORD_w1_2$q8_no_inidcoll),'1'=1L,'2'=1L,'3'=0L,'4'=0L)
table(env_RECORD_0$env_nbh_belong_0) 

```
### **Variable label**: Belonging to neighbourhood        
**Variable name**: env_nbh_belong_1        
**Variable description**: Indicator of whether the participant asked whether they feel a part of the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not feel part of area
1 | Feels part of area     
   

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Belonging to neighbourhood        
**Variable name**: env_nbh_belong_2      
**Variable description**: Indicator of whether the participant asked whether they feel a part of the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not feel part of area  
1 | Feels part of area     
     

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Belonging to neighbourhood        
**Variable name**: env_nbh_belong_3        
**Variable description**: Indicator of whether the participant asked whether they feel a part of the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not feel part of area  
1 | Feels part of area     
     

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Belonging to neighbourhood        
**Variable name**: env_nbh_belong_4      
**Variable description**: Indicator of whether the participant asked whether they feel a part of the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not feel part of area 
1 | Feels part of area     
   

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_0      
**Variable description**: Indicator of whether the participant agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that they feel lonely   
2 | Agree that they feel lonely
3 | Neither agree or disagree that they feel lonely 
4 | Disagree that they feel lonely  
5 | Strongly disagree that they feel lonely         

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_1      
**Variable description**: Indicator of whether the participant agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that they feel lonely   
2 | Agree that they feel lonely
3 | Neither agree or disagree that they feel lonely 
4 | Disagree that they feel lonely  
5 | Strongly disagree that they feel lonely         

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_2      
**Variable description**: Indicator of whether the participant agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that they feel lonely   
2 | Agree that they feel lonely
3 | Neither agree or disagree that they feel lonely 
4 | Disagree that they feel lonely 
5 | Strongly disagree that they feel lonely         

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_3      
**Variable description**: Indicator of whether the participant agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that they feel lonely   
2 | Agree that they feel lonely
3 | Neither agree or disagree that they feel lonely  
4 | Disagree that they feel lonely   
5 | Strongly disagree that they feel lonely        

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_4      
**Variable description**: Indicator of whether the participant agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that they feel lonely   
2 | Agree that they feel lonely
3 | Neither agree or disagree that they feel lonely 
4 | Disagree that they feel lonely  
5 | Strongly disagree that they feel lonely         

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Close-knit community        
**Variable name**: env_nbh_comm_0      
**Variable description**: Indicator of whether the participant agrees that members of the area in which participant lives are close-knit (community solidarity).        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strong neighbourhood solidarity     
2 | Some neighbourhood solidarity    
3 | A little neighbourhood solidarity    
4 | No neighbourhood solidarity                   

**Harmonization status**:   complete 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(RECORD_w1_2$q11_no_habsoude)
summary(RECORD_w1_2$q11_no_habsoude)
#not an integer
#1 and 2 = agree, solidarity ,  3 and 4=disagree
env_RECORD_0$env_nbh_comm_0 <-recode(as.integer(RECORD_w1_2$q11_no_habsoude),'1'=1L,'2'=2L,'3'=3L,'4'=4L)
table(env_RECORD_0$env_nbh_comm_0)

``` 
### **Variable label**: Close-knit community        
**Variable name**: env_nbh_comm_1      
**Variable description**: Indicator of whether the participant agrees that members of the area in which participant lives are close-knit (community solidarity).       
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strong neighbourhood solidarity     
2 | Some neighbourhood solidarity    
3 | A little neighbourhood solidarity    
4 | No neighbourhood solidarity                   

**Harmonization status**:   complete 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(RECORD_w2$P48_Q2_1060) #1= Inhabitants definitely live apart in neighbourhood
table(RECORD_w2$P48_Q2_1061)
table(RECORD_w2$P48_Q2_1062)
table(RECORD_w2$P48_Q2_1063) #4 Inhabitants don't live apart in neighbourhood at all

env_RECORD_1$env_nbh_comm_1  <- as.integer(ifelse(RECORD_w2$P48_Q2_1060 == '1', 4,                                                                                                                      (ifelse (RECORD_w2$P48_Q2_1061 == '1', 3,
                                                         (ifelse (RECORD_w2$P48_Q2_1062 == '1', 2,
                                                                 (ifelse (RECORD_w2$P48_Q2_1063 == '1', 1, NA))))))))
table(env_RECORD_1$env_nbh_comm_1)

``` 
### **Variable label**: Close-knit community        
**Variable name**: env_nbh_comm_2      
**Variable description**: Indicator of whether the participant agrees that members of the area in which participant lives are close-knit (community solidarity).       
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strong neighbourhood solidarity     
2 | Some neighbourhood solidarity    
3 | A little neighbourhood solidarity    
4 | No neighbourhood solidarity                   

**Harmonization status**:   impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Close-knit community        
**Variable name**: env_nbh_comm_3      
**Variable description**: Indicator of whether the participant agrees that members of the area in which participant lives are close-knit (community solidarity).      
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strong neighbourhood solidarity     
2 | Some neighbourhood solidarity    
3 | A little neighbourhood solidarity    
4 | No neighbourhood solidarity                   

**Harmonization status**:   impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Close-knit community        
**Variable name**: env_nbh_comm_4      
**Variable description**: Indicator of whether the participant agrees that members of the area in which participant lives are close-knit (community solidarity).      
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strong neighbourhood solidarity     
2 | Some neighbourhood solidarity    
3 | A little neighbourhood solidarity    
4 | No neighbourhood solidarity                   

**Harmonization status**:   impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
# Neighbourhood aesthetics subdomain

### **Variable label**: Neighbourhood cleanliness (4-level)    
**Variable name**:  env_nbh_clean_0  
**Variable description**:  Indicator of the participant's perception of the cleanliness (presence of rubbish) of the area where the respondent lives (i.e. their neighbourhood).      
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Area not very clean     
2 | Area not clean   
3 | Area mostly clean   
4 | Area clean             

**Harmonization status**:   complete 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(RECORD_w1_2$q10_no_pbordure)
#1 and 2 = yes, garbage 
env_RECORD_0$env_nbh_clean_0 <-recode(as.integer(RECORD_w1_2$q10_no_pbordure),'1'=1L,'2'=2L,'3'=3L,'4'=4L)
table(env_RECORD_0$env_nbh_clean_0)

```
### **Variable label**: Neighbourhood cleanliness (4-level)    
**Variable name**:  env_nbh_clean_1  
**Variable description**:  Indicator of the participant's perception of the cleanliness (presence of rubbish) of the area where the respondent lives (i.e. their neighbourhood).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Area not very clean     
2 | Area not clean   
3 | Area mostly clean   
4 | Area clean             

**Harmonization status**:   complete 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(RECORD_w2$P43_Q5_960) #1= rubbish 
table(RECORD_w2$P43_Q5_961)  #1= rubbish 
table(RECORD_w2$P43_Q5_962)  #1= not really 1162
table(RECORD_w2$P43_Q5_963)   #1= not  1726 

env_RECORD_1$env_nbh_clean_1 <- as.integer(ifelse(RECORD_w2$P43_Q5_960 == '1', 1,                                                                            (ifelse (RECORD_w2$P43_Q5_961 == '1', 2,
                                                         (ifelse (RECORD_w2$P43_Q5_962 == '1', 3,
                                                                 (ifelse (RECORD_w2$P43_Q5_963 == '1', 4, NA))))))))
table(env_RECORD_1$env_nbh_clean_1)

```
### **Variable label**: Neighbourhood cleanliness (2-level)      
**Variable name**:  env_nbh_clean_dich_0  
**Variable description**:  Indicator of the participant's perception of the cleanliness (presence of rubbish) of the area where respondent lives (i.e. their neighbourhood), dichotomized.       
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Area not clean  
1 | Area clean             


**Harmonization status**:   complete 
**Harmonization comment**:   'No, not really' rubbish was coded as area clean. 'Yes, a bit of rubbish' was recoded as 'area not clean'.
**R script**:  
```{r, echo=TRUE}
table(RECORD_w1_2$q10_no_pbordure)
#1 and 2 = yes, garbage 
env_RECORD_0$env_nbh_clean_dich_0<-recode(as.integer(RECORD_w1_2$q10_no_pbordure),'1'=0L,'2'=0L,'3'=1L,'4'=1L)
table(env_RECORD_0$env_nbh_clean_dich_0)

```
### **Variable label**: Neighbourhood cleanliness (2-level)       
**Variable name**:  env_nbh_clean_dich_1    
**Variable description**:  Indicator of the participant's perception of the cleanliness (presence of rubbish) of the area where respondent lives (i.e. their neighbourhood), dichotomized.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Area not clean 
1 | Area clean             
 

**Harmonization status**:   complete 
**Harmonization comment**:  'No, not really' rubbish was coded as area clean. 'Yes, a bit of rubbish' was recoded as 'area not clean'.
**R script**:  
```{r, echo=TRUE}
table(RECORD_w2$P43_Q5_960) #1= rubbish 462
RECORD_w2$P43_Q5_960 <-as.integer(RECORD_w2$P43_Q5_960)
summary(RECORD_w2$P43_Q5_960)

table(RECORD_w2$P43_Q5_961)  #1= rubbish 1162
RECORD_w2$P43_Q5_961 <-as.integer(RECORD_w2$P43_Q5_961)
summary(RECORD_w2$P43_Q5_961)

table(RECORD_w2$P43_Q5_962)  #1= not really 3107
RECORD_w2$P43_Q5_962 <-as.integer(RECORD_w2$P43_Q5_962)
summary(RECORD_w2$P43_Q5_962)

table(RECORD_w2$P43_Q5_963)   #1= not  1726 
RECORD_w2$P43_Q5_963 <-as.integer(RECORD_w2$P43_Q5_963)
summary(RECORD_w2$P43_Q5_963)

env_RECORD_1$env_nbh_clean_dich_1 <- as.integer(ifelse((RECORD_w2$P43_Q5_960 == '1' | RECORD_w2$P43_Q5_961 == '1'), 0,                                               (ifelse (RECORD_w2$P43_Q5_962 == '1' | RECORD_w2$P43_Q5_963 == '1', 1, NA))))
table(env_RECORD_1$env_nbh_clean_dich_1)
summary(env_RECORD_1$env_nbh_clean_dich_1)
#not clean should be 1162+462=1624 , clean should be 1726+3107=4833, check but why is there 1 NA?!!!!

#one person said 0 to all 4 variables, thus I consider this person as if they did not answer these 4 qs, 
#cannot know what they meant 

```
### **Variable label**: Neighbourhood cleanliness (2-level)      
**Variable name**:  env_nbh_clean_dich_2    
**Variable description**:  Indicator of the participant's perception of the cleanliness (presence of rubbish) of the area where respondent lives (i.e. their neighbourhood), dichotomized.       
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Area not clean 
1 | Area clean             
 

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```

### **Variable label**: Neighbourhood noisiness (4-level)       
**Variable name**:  env_nbh_noise_0  
**Variable description**:  Indicator of the participant's perception of presence of excessive noise in their neighbourhood.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Definitely excessive noise      
2 | Some excessive noise    
3 | A little excessive noise    
4 | No excessive noise            

**Harmonization status**:   complete
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(RECORD_w1_2$q10_no_bruitgen)
summary(RECORD_w1_2$q10_no_bruitgen)
#not an integer
#1 and 2 = yes noise,  3 and 4=no noise 
env_RECORD_0$env_nbh_noise_0 <-recode(as.integer(RECORD_w1_2$q10_no_bruitgen),'1'=1L,'2'=2L,'3'=3L,'4'=4L)
table(env_RECORD_0$env_nbh_noise_0)

```
### **Variable label**: Neighbourhood noisiness (4-level)       
**Variable name**:  env_nbh_noise_1  
**Variable description**:  Indicator of the participant's perception of presence of excessive noise in their neighbourhood.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Definitely excessive noise      
2 | Some excessive noise    
3 | A little excessive noise    
4 | No excessive noise            

**Harmonization status**:   complete
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(RECORD_w2$P43_Q2_945) #1= excessive noise 
table(RECORD_w2$P43_Q2_946)  #1= noise 
table(RECORD_w2$P43_Q2_947)  #1= not really 
table(RECORD_w2$P43_Q2_948)   #1= not  

env_RECORD_1$env_nbh_noise_1 <- as.integer(ifelse(RECORD_w2$P43_Q2_945 == '1', 1,                                                                                                              (ifelse (RECORD_w2$P43_Q2_946 == '1', 2,
                                                         (ifelse (RECORD_w2$P43_Q2_947 == '1', 3,
                                                                 (ifelse (RECORD_w2$P43_Q2_948 == '1', 4, NA))))))))
table(env_RECORD_1$env_nbh_noise_1)

```
### **Variable label**: Neighbourhood noisiness (2-level)       
**Variable name**:  env_nbh_noise_dich_0    
**Variable description**:  Indicator of the participant's perception of presence of excessive noise in their neighbourhood, dichotomized. 
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
------------- | -------------  
0 | Noisy 
1 | Not noisy         


**Harmonization status**:   complete
**Harmonization comment**: 
**R script**:  
```{r, echo=TRUE}
table(RECORD_w1_2$q10_no_bruitgen)
summary(RECORD_w1_2$q10_no_bruitgen)
#not an integer
#1 and 2 = yes noise,  3 and 4=no noise 
env_RECORD_0$env_nbh_noise_dich_0 <-recode(as.integer(RECORD_w1_2$q10_no_bruitgen),'1'=0L,'2'=0L,'3'=1L,'4'=1L)
table(env_RECORD_0$env_nbh_noise_dich_0)

```
### **Variable label**: Neighbourhood noisiness (2-level)     
**Variable name**:  env_nbh_noise_dich_1  
**Variable description**:  Indicator of the participant's perception of presence of excessive noise in their neighbourhood, dichotomized.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
------------- | -------------  
0 | Noisy  
1 | Not noisy         


**Harmonization status**:   complete
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
table(RECORD_w2$P43_Q2_945) #1= excessive noise 
table(RECORD_w2$P43_Q2_946)  #1= noise 
table(RECORD_w2$P43_Q2_947)  #1= not really 
table(RECORD_w2$P43_Q2_948)   #1= not  

env_RECORD_1$env_nbh_noise_dich_1 <- as.integer(ifelse((RECORD_w2$P43_Q2_945 == '1' | RECORD_w2$P43_Q2_946 == '1'), 0,
                                                         (ifelse (RECORD_w2$P43_Q2_947 == '1'| RECORD_w2$P43_Q2_948 == '1', 1, NA))))

table(env_RECORD_1$env_nbh_noise_dich_1)

```
### **Variable label**: Neighbourhood traffic noise        
**Variable name**:  env_nbh_traf_noise_0    
**Variable description**:  Indicator of  the participant's perception of presence of noise from traffic, in their neighbourhood.            
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
------------- | -------------  
0 | Traffic noise 
1 | No traffic noise         


**Harmonization status**:   impossible
**Harmonization comment**: 
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbourhood traffic noise      
**Variable name**:  env_nbh_traf_noise_1  
**Variable description**:  Indicator of  the participant's perception of presence of noise from traffic, in their neighbourhood.           
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
------------- | -------------  
0 | Traffic noise 
1 | No traffic noise         


**Harmonization status**:   complete
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
table(RECORD_w2$P40_Q2_881) #1= Not at all traffic noise neighbourhoo 
table(RECORD_w2$P40_Q2_882)  #1= somewhat traffic noise 
table(RECORD_w2$P40_Q2_883)  #1= not really traffic 
table(RECORD_w2$P40_Q2_885)   #1= Definitely traffic noise neighbourhood  

env_RECORD_1$env_nbh_traf_noise_1 <- as.integer(ifelse((RECORD_w2$P40_Q2_881 == '1' | RECORD_w2$P40_Q2_883 == '1'), 1,
                                                         (ifelse (RECORD_w2$P40_Q2_882 == '1'| RECORD_w2$P40_Q2_885 == '1', 0, NA))))

table(env_RECORD_1$env_nbh_traf_noise_1)

```
# Crime and vandalism subdomain

### **Variable label**: Neighbourhood violence  
**Variable name**: env_nbh_violence_0     
**Variable description**:  Indicator of the participant's perception of violence in their neighbourhood.  
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Violence in neighbourhood  
1 | No violence in neighbourhood
   

**Harmonization status**:   impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbourhood violence  
**Variable name**: env_nbh_violence_1     
**Variable description**: Indicator of the participant's perception of violence in their neighbourhood.       
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Violence in neighbourhood
1 | No violence in neighbourhood
     

**Harmonization status**:   complete 
**Harmonization comment**:  RECORD participants were asked if they heard  about gunshots, rape, burglary, gangs, burning cars, in the neighbourhood, if yes then this was coded as presence of violence in the neighbourhood.   
**R script**:  
```{r, echo=TRUE}
table(RECORD_w2$P46_Q5_1028)	# Heard about gunshots fired in neighbourhood
table(RECORD_w2$P46_Q5_1029)   #not heard P46_Q3_1022
table(RECORD_w2$P46_Q3_1022) #rape P46_Q3_1022
table(RECORD_w2$P46_Q3_1023) #have not heard of rape
table(RECORD_w2$P46_Q6_1030)  # Haven't heard about burglary in neighbourhood
table(RECORD_w2$P46_Q6_1031)  #Heard about burglary in neighbourhood
table(RECORD_w2$P44_Q5_987)  #Definitely gangs make law in neighbourhood
table(RECORD_w2$P44_Q5_988)
table(RECORD_w2$P44_Q5_989)
table(RECORD_w2$P44_Q5_990)  # no gang 
table(RECORD_w2$P46_Q4_1024) #1 = no haven't heard about burning car in neighbourhood
table(RECORD_w2$P46_Q4_1025) #1 = yes heard about burning car in neighbourhood

env_RECORD_1$env_nbh_violence_1  <- as.integer(ifelse((RECORD_w2$P46_Q5_1028 == '1' | RECORD_w2$P46_Q3_1022 == '1' | RECORD_w2$P46_Q6_1031 == '1' | RECORD_w2$P44_Q5_987 == '1'| RECORD_w2$P44_Q5_988 == '1'| RECORD_w2$P46_Q4_1025 == '1'), 0,                                      
                                                      (ifelse (RECORD_w2$P46_Q5_1029 == '1' | RECORD_w2$P46_Q3_1023 == '1'| RECORD_w2$P46_Q6_1030 == '1'| RECORD_w2$P44_Q5_989 == '1'| RECORD_w2$P44_Q5_990 == '1' | RECORD_w2$P46_Q4_1024 == '1',1, NA))))

table(env_RECORD_1$env_nbh_violence_1)

```
### **Variable label**: Neighbourhood violence  
**Variable name**: env_nbh_violence_2     
**Variable description**: Indicator of the participant's perception of violence in their neighbourhood.      
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Violence in neighbourhood  
1 | No violence in neighbourhood
   

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbourhood antisocial and aggressive behaviour 
**Variable name**: env_nbs_anti_0  
**Variable description**: Indicator of the participant's perception of antisocial and aggressive behaviour in their neighbourhood.    
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Antisocial and aggressive behavior in neighbourhood 
1 | No antisocial and aggressive behavior in neighbourhood
     

**Harmonization status**:   Complete
**Harmonization comment**:  Similarly to GLOBE, the RECORD variable refers to youth nuisance.  
**R script**:  
```{r, echo=TRUE}
env_RECORD_0$env_nbs_anti_0 <-recode(as.integer(RECORD_w1_2$q10_no_incivili),'1'=0L,'2'=0L,'3'=1L,'4'=1L)
```
### **Variable label**: Neighbourhood antisocial and aggressive behaviour 
**Variable name**: env_nbs_anti_1  
**Variable description**: Indicator of the participant's perception of antisocial and aggressive behaviour in their neighbourhood.   
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Antisocial and aggressive behavior in neighbourhood 
1 | No antisocial and aggressive behavior in neighbourhood
     

**Harmonization status**:   complete
**Harmonization comment**:  Similarly to GLOBE, the RECORD variable refers to youth nuisance. 
**R script**:  
```{r, echo=TRUE}
env_RECORD_1$env_nbs_anti_1 <- as.integer(ifelse((RECORD_w2$P43_Q1_942 == '1' | RECORD_w2$P43_Q1_943 == '1'), 1,                                               (ifelse (RECORD_w2$P43_Q1_940 == '1' | RECORD_w2$P43_Q1_941 == '1', 0, NA))))

```
### **Variable label**: Neighbourhood antisocial and aggressive behaviour 
**Variable name**: env_nbs_anti_2  
**Variable description**: Indicator of the participant's perception of antisocial and aggressive behaviour in their neighbourhood.    
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Antisocial and aggressive behavior in neighbourhood  
1 | No antisocial and aggressive behavior in neighbourhood
    

**Harmonization status**:   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbourhood graffiti and vandalism  
**Variable name**:  env_nbh_gv_0  
**Variable description**:  Indicator of the participant's perception of graffiti and/or vandalism in the area where the respondent lives (i.e. their neighbourhood).    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | No graffiti and no vandalism 
1 | Graffiti and/or vandalism   
             

**Harmonization status**:   complete 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(RECORD_w1_2$q10_no_vandalis)
summary(RECORD_w1_2$q10_no_vandalis)
#not an integer
#1 and 2 = yes vandalism and graffiti,  3 and 4=none
env_RECORD_0$env_nbh_gv_0 <-recode(as.integer(RECORD_w1_2$q10_no_vandalis),'1'=1L,'2'=1L,'3'=0L,'4'=0L)
table(env_RECORD_0$env_nbh_gv_0)

```
### **Variable label**: Neighbourhood graffiti and vandalism  
**Variable name**:  env_nbh_gv_1    
**Variable description**:  Indicator of the participant's perception of graffiti and/or vandalism in the area where the respondent lives (i.e. their neighbourhood).   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | No graffiti and no vandalism 
1 | Graffiti and/or vandalism   
             

**Harmonization status**:   complete 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(RECORD_w2$P44_Q2_972) #1= graf and vand
table(RECORD_w2$P44_Q2_973)  #1= graf and vand 
table(RECORD_w2$P44_Q2_974)  #1= not
table(RECORD_w2$P44_Q2_975)   #1= not    
 
env_RECORD_1$env_nbh_gv_1 <- as.integer(ifelse((RECORD_w2$P44_Q2_972 == '1' | RECORD_w2$P44_Q2_973 == '1'), 1,                                               (ifelse (RECORD_w2$P44_Q2_974 == '1' | RECORD_w2$P44_Q2_975 == '1', 0, NA))))
table(env_RECORD_1$env_nbh_gv_1)
summary(env_RECORD_1$env_nbh_gv_1)

```
### **Variable label**: Neighbourhood graffiti and vandalism    
**Variable name**:  env_nbh_gv_2  
**Variable description**:  Indicator of the participant's perception of graffiti and/or vandalism in the area where the respondent lives (i.e. their neighbourhood).   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | No graffiti and no vandalism 
1 | Graffiti and/or vandalism    
           

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Theft of transportation method   
**Variable name**: env_nbh_theft_0     
**Variable description**:  Indicator of the participant's perception of the occurrence of theft of transport vehicle in their neighbourhood.  
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Theft of vehicle in neighbourhood  
1 | No theft of vehicle in neighbourhood


**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Theft of transportation method   
**Variable name**: env_nbh_theft_1     
**Variable description**: Indicator of the participant's perception of the occurrence of theft of transport vehicle in their neighbourhood.         
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
------------- | -------------  
0 | Theft of vehicle in neighbourhood  
1 | No theft of vehicle in neighbourhood


**Harmonization status**:   complete
**Harmonization comment**:   RECORD asks if respondent has heard or not about vehicle theft. 
**R script**:  
```{r, echo=TRUE}
table(RECORD_w2$P46_Q1_1016) # 1=heard about theft 
table(RECORD_w2$P46_Q1_1017) #2 1= not heard
env_RECORD_1$env_nbh_theft_1 <- as.integer(ifelse((RECORD_w2$P46_Q1_1016 == '1'), 0,                                              
                                                  (ifelse (RECORD_w2$P46_Q1_1017 == '1', 1, NA))))
table(env_RECORD_1$env_nbh_theft_1)

```
### **Variable label**: Theft of transportation method   
**Variable name**: env_nbh_theft_2     
**Variable description**: Indicator of the participant's perception of the occurrence of theft of transport vehicle in their neighbourhood.        
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Theft of vehicle in neighbourhood  
1 | No theft of vehicle in neighbourhood


**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
