---
title: "Perceptions of urban environment DataSchema"
output: html_document
---
# Table of Contents
1. [General neighborhood safety subdomain](#general-neighborhood-safety-subdomain)
2. [Social trust subdomain](#social-trust-subdomain)
3. [Vandalism subdomain](#vandalism-subdomain)
4. [Social cohesion subdomain](#social-cohesion-subdomain)

# General neighborhood safety subdomain

### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsafe_0   
**Variable description**:  Respondent agrees that they feel safe at night in the area where they live (i.e. their neighbourhood)   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   yes  
0 |   no  
-999 | missing 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsafe_1   
**Variable description**:  Respondent agrees that they feel safe at night in the area where they live (i.e. their neighbourhood)   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   yes  
0 |   no  
-999 | missing 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsafe_2   
**Variable description**:  Respondent agrees that they feel safe at night in the area where they live (i.e. their neighbourhood)   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   yes  
0 |   no  
-999 | missing 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsafe_3   
**Variable description**:  Respondent agrees that they feel safe at night in the area where they live (i.e. their neighbourhood)   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   yes  
0 |   no  
-999 | missing 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsafe_4   
**Variable description**:  Respondent agrees that they feel safe at night in the area where they live (i.e. their neighbourhood)   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   yes  
0 |   no  
-999 | missing 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsafe_5   
**Variable description**:  Respondent agrees that they feel safe at night in the area where they live (i.e. their neighbourhood)   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   yes  
0 |   no  
-999 | missing 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsafe_6   
**Variable description**:  Respondent agrees that they feel safe at night in the area where they live (i.e. their neighbourhood)   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   yes  
0 |   no  
-999 | missing 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe in the neighbourhood     
**Variable name**: env_nbh_sf_0   
**Variable description**:  Respondent agrees that they feel safe in their neighbourhood   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | yes  
0 | no  
-999 | missing 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe in the neighbourhood     
**Variable name**: env_nbh_sf_2   
**Variable description**:  Respondent agrees that they feel safe in their neighbourhood   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | yes  
0 | no  
-999 | missing 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Neighbourhood violence   
**Variable name**: env_nbh_violence_0   
**Variable description**:  Respondent’s perception of presence of violence  in their neighbourhood   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   a lot of violence 
2 |   some violence
3 |   a little violence 
4 |   no violence 
-999 | missing 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
# Social trust subdomain

### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_0   
**Variable description**:  Respondent is asked if most people in the area where they live  (i.e. in their neighbourhood)  can be trusted  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | yes    
0 | no     
-999 | missing   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_1   
**Variable description**:  Respondent is asked if most people in the area where they live  (i.e. in their neighbourhood)  can be trusted  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | yes    
0 | no     
-999 | missing   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_2     
**Variable description**:  Respondent is asked if most people in the area where they live  (i.e. in their neighbourhood)  can be trusted  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | yes    
0 | no     
-999 | missing   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_4     
**Variable description**:  Respondent is asked if most people in the area where they live  (i.e. in their neighbourhood)  can be trusted  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | yes    
0 | no     
-999 | missing   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```


# Vandalism subdomain

### **Variable label**: Neighbourhood cleanliness   
**Variable name**:  env_nbh_clean_0  
**Variable description**:  Respondent perception of the cleanliness (presence of rubbish) of the area where respondent lives (i.e. their neighbourhood)  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Not very clean     
2 | Not clean   
3 | Mostly clean   
4 | Clean      
-999 | missing        

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood graffiti and vandalism  
**Variable name**:  env_nbh_grfvnd_0  
**Variable description**:  Respondent perception of the cleanliness (presence of rubbish) of the area where respondent lives (i.e. their neighbourhood)  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | A lot of graffiti and vandalism      
2 | Some graffiti and vandalism     
3 | A little graffiti and vandalism     
4 | No graffiti and vandalism       
-999 | missing        

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood noise    
**Variable name**:  env_nbh_noise_0  
**Variable description**:  Respondent’s perception of presence of excessive noise in their neighbourhood     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Definitely excessive noise      
2 | Some excessive noise    
3 | A little excessive noise    
4 | No excessive noise     
-999 | missing        

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood noise    
**Variable name**:  env_nbh_noise_1  
**Variable description**:  Respondent’s perception of presence of excessive noise in their neighbourhood     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Definitely excessive noise      
2 | Some excessive noise    
3 | A little excessive noise    
4 | No excessive noise     
-999 | missing        

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
# Social cohesion subdomain

### **Variable label**: Helpful neighbours  
**Variable name**: env_nbs_help_0  
**Variable description**: Respondent agrees that neighbors would help them if needed, in case of emergency/trouble  
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | yes    
0 | no     
-999 | missing  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Helpful neighbours  
**Variable name**: env_nbs_help_2  
**Variable description**: Respondent agrees that neighbors would help them if needed,  in case of emergency/trouble  
**Value type**: integer   
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | yes    
0 | no     
-999 | missing  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Helpful neighbours  
**Variable name**: env_nbs_help_4  
**Variable description**: Respondent agrees that neighbors would help them if needed,  in case of emergency/trouble  
**Value type**: integer   
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | yes    
0 | no     
-999 | missing  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Neighbours cooperate  
**Variable name**: env_nbs_coop_0   
**Variable description**: Respondent agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out  
**Value type**: integer  
**Variable unit**: N/A   
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | yes    
0 | no     
-999 | missing    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Neighbours cooperate    
**Variable name**: env_nbs_coop_1  
**Variable description**: Respondent agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out    
**Value type**: integer    
**Variable unit**: N/A     
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | yes    
0 | no     
-999 | missing      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Neighbours cooperate    
**Variable name**: env_nbs_coop_2  
**Variable description**: Respondent agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out    
**Value type**: integer    
**Variable unit**: N/A     
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | yes    
0 | no     
-999 | missing      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbours cooperate    
**Variable name**: env_nbs_coop_3  
**Variable description**: Respondent agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out    
**Value type**: integer    
**Variable unit**: N/A     
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | yes    
0 | no     
-999 | missing      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Neighbours cooperate    
**Variable name**: env_nbs_coop_4  
**Variable description**: Respondent agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out    
**Value type**: integer    
**Variable unit**: N/A     
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | yes    
0 | no     
-999 | missing      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Neighbourhood values and norms       
**Variable name**: env_nbh_values_0   
**Variable description**: Respondent agrees that people in their neighbourhood share similar values and norms        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree    
2 | Agree 
3 | Neither agree or disagree  
4 | Disagree   
5 | Strongly disagree   
-999 | missing      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Neighbourhood values and norms       
**Variable name**: env_nbh_values_2     
**Variable description**: Respondent agrees that people in their neighbourhood share similar values and norms        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree    
2 | Agree 
3 | Neither agree or disagree  
4 | Disagree   
5 | Strongly disagree   
-999 | missing      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood values and norms       
**Variable name**: env_nbh_values_4     
**Variable description**: Respondent agrees that people in their neighbourhood share similar values and norms        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree    
2 | Agree 
3 | Neither agree or disagree  
4 | Disagree   
5 | Strongly disagree   
-999 | missing      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_0   
**Variable description**: Respondent agrees that people in their neighbourhood  get along with each other        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree    
2 | Agree 
3 | Neither agree or disagree  
4 | Disagree   
5 | Strongly disagree   
-999 | missing      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_2   
**Variable description**: Respondent agrees that people in their neighbourhood  get along with each other        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree    
2 | Agree 
3 | Neither agree or disagree  
4 | Disagree   
5 | Strongly disagree   
-999 | missing      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_3   
**Variable description**: Respondent agrees that people in their neighbourhood  get along with each other        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree    
2 | Agree 
3 | Neither agree or disagree  
4 | Disagree   
5 | Strongly disagree   
-999 | missing      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_4   
**Variable description**: Respondent agrees that people in their neighbourhood  get along with each other        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree    
2 | Agree 
3 | Neither agree or disagree  
4 | Disagree   
5 | Strongly disagree   
-999 | missing      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbours are friendly       
**Variable name**: env_nbs_friend_0     
**Variable description**: Respondent is asked whether members of the area where their live (i.e. their neighbourhood) are friendly/ polite           
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Friendly    
2 | Somewhat friendly 
3 | Not really friendly  
4 | Not friendly    
-999 | missing  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Belonging to neighbourhood        
**Variable name**: env_nbh_belong_0      
**Variable description**: Respondent asked whether they feel a part of the area where they live (i.e. their community, their neighbourhood)    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Yes    
0 | No   
-999 | missing  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Belonging to neighbourhood        
**Variable name**: env_nbh_belong_2      
**Variable description**: Respondent asked whether they feel a part of the area where they live (i.e. their community, their neighbourhood)    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Yes    
0 | No   
-999 | missing  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Belonging to neighbourhood        
**Variable name**: env_nbh_belong_4      
**Variable description**: Respondent asked whether they feel a part of the area where they live (i.e. their community, their neighbourhood)    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Yes    
0 | No   
-999 | missing  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_0      
**Variable description**: Respondent agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood)    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree    
2 | Agree 
3 | Neither agree or disagree  
4 | Disagree   
5 | Strongly disagree   
-999 | missing        

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_2      
**Variable description**: Respondent agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood)    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree    
2 | Agree 
3 | Neither agree or disagree  
4 | Disagree   
5 | Strongly disagree   
-999 | missing        

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_3      
**Variable description**: Respondent agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood)    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree    
2 | Agree 
3 | Neither agree or disagree  
4 | Disagree   
5 | Strongly disagree   
-999 | missing        

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_4      
**Variable description**: Respondent agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood)    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree    
2 | Agree 
3 | Neither agree or disagree  
4 | Disagree   
5 | Strongly disagree   
-999 | missing        

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
