---
title: "Perceptions of urban environment DataSchema"
output: html_document
---
# Table of Contents

1. [General neighborhood safety subdomain](#general-neighborhood-safety-subdomain)
2. [Social trust subdomain](#social-trust-subdomain)
3. [Social cohesion subdomain](#social-cohesion-subdomain)  
4. [Neighbourhood aesthetics subdomain](#vandalism-subdomain)
5. [Crime & vandalism subdomain](#crime-subdomain)  

# General neighborhood safety subdomain

### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsafe_0   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   Feels safe at night  
0 |   Does not feel safe at night  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsafe_1   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   Feels safe at night  
0 |   Does not feel safe at night 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsafe_2   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   Feels safe at night  
0 |   Does not feel safe at night 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsafe_3   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   Feels safe at night  
0 |   Does not feel safe at night 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsafe_4   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   Feels safe at night  
0 |   Does not feel safe at night 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsafe_5   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   Feels safe at night  
0 |   Does not feel safe at night 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsafe_6   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   Feels safe at night  
0 |   Does not feel safe at night  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_0   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood. Note: GLOBE variable used is the version which asks about daytime safety, RECORD does not denote time of day, HAPIEE and LASA ask about night time safety.      
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   Feels safe 
0 |   Does not feel safe  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_1   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood. Note: GLOBE variable used is the version which asks about daytime safety, RECORD does not denote time of day, HAPIEE and LASA ask about night time safety.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   Feels safe 
0 |   Does not feel safe  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_2   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood. Note: GLOBE variable used is the version which asks about daytime safety, RECORD does not denote time of day, HAPIEE and LASA ask about night time safety.     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   Feels safe 
0 |   Does not feel safe   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_3   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood. Note: GLOBE variable used is the version which asks about daytime safety, RECORD does not denote time of day, HAPIEE and LASA ask about night time safety.     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   Feels safe 
0 |   Does not feel safe   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_4   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood. Note: GLOBE variable used is the version which asks about daytime safety, RECORD does not denote time of day, HAPIEE and LASA ask about night time safety.     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   Feels safe 
0 |   Does not feel safe   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_5   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood. Note: GLOBE variable used is the version which asks about daytime safety, RECORD does not denote time of day, HAPIEE and LASA ask about night time safety.     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   Feels safe 
0 |   Does not feel safe   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_6   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood. Note: GLOBE variable used is the version which asks about daytime safety, RECORD does not denote time of day, HAPIEE and LASA ask about night time safety.     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   Feels safe 
0 |   Does not feel safe   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
# Social trust subdomain

### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_0   
**Variable description**:  Indicator of whether the participant is asked if most people in the area where they live  (i.e. in their neighbourhood)  can be trusted.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | People can be trusted    
0 | People cannot be trusted         

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_1   
**Variable description**:  Indicator of whether the participant is asked if most people in the area where they live  (i.e. in their neighbourhood)  can be trusted.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | People can be trusted    
0 | People cannot be trusted       

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_2     
**Variable description**:  Indicator of whether the participant is asked if most people in the area where they live  (i.e. in their neighbourhood)  can be trusted.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | People can be trusted    
0 | People cannot be trusted      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_4     
**Variable description**:  Indicator of whether the participant is asked if most people in the area where they live  (i.e. in their neighbourhood)  can be trusted.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | People can be trusted    
0 | People cannot be trusted       

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Social cohesion subdomain

### **Variable label**: Helpful neighbours  
**Variable name**: env_nbs_help_0  
**Variable description**: Indicator of whether the participant agrees that neighbors would help them if needed, in case of emergency/trouble.  
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Neighbours would help me   
0 | Neighbours would not help me       

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Helpful neighbours  
**Variable name**: env_nbs_help_2  
**Variable description**: Indicator of whether the participant agrees that neighbors would help them if needed,  in case of emergency/trouble.  
**Value type**: integer   
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Neighbours would help me    
0 | Neighbours would not help me         

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Helpful neighbours  
**Variable name**: env_nbs_help_4  
**Variable description**: Indicator of whether the participant agrees that neighbors would help them if needed,  in case of emergency/trouble.  
**Value type**: integer   
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Neighbours would help me   
0 | Neighbours would not help me      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Neighbours cooperate  
**Variable name**: env_nbs_coop_0   
**Variable description**: Indicator of whether the participant agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out.  
**Value type**: integer  
**Variable unit**: N/A   
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | People willing to help each other   
0 | People not willing to help each other         

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Cooperating neighbours    
**Variable name**: env_nbs_coop_1  
**Variable description**: Indicator of whether the participant agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out.    
**Value type**: integer    
**Variable unit**: N/A     
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | People willing to help each other   
0 | People not willing to help each other             

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Cooperating neighbours      
**Variable name**: env_nbs_coop_2  
**Variable description**: Indicator of whether the participant agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out.    
**Value type**: integer    
**Variable unit**: N/A     
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | People willing to help each other   
0 | People not willing to help each other               

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Cooperating neighbours      
**Variable name**: env_nbs_coop_3  
**Variable description**: Indicator of whether the participant agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out.    
**Value type**: integer    
**Variable unit**: N/A     
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | People willing to help each other   
0 | People not willing to help each other            

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Cooperating neighbours      
**Variable name**: env_nbs_coop_4  
**Variable description**: Indicator of whether the participant agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out.    
**Value type**: integer    
**Variable unit**: N/A     
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | People willing to help each other   
0 | People not willing to help each other             

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Neighbourhood values and norms       
**Variable name**: env_nbh_values_0   
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood share similar values and norms.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people share similar values and norms    
2 | Agree that people share similar values and norms
3 | Neither agree or disagree that people share similar values and norms
4 | Disagree that people share similar values and norms  
5 | Strongly disagree that people share similar values and norms        

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Neighbourhood values and norms       
**Variable name**: env_nbh_values_2     
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood share similar values and norms.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people share similar values and norms   
2 | Agree that people share similar values and norms
3 | Neither agree or disagree that people share similar values and norms  
4 | Disagree that people share similar values and norms  
5 | Strongly disagree that people share similar values and norms       

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood values and norms       
**Variable name**: env_nbh_values_4     
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood share similar values and norms.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people share similar values and norms   
2 | Agree that people share similar values and norms
3 | Neither agree or disagree that people share similar values and norms 
4 | Disagree that people share similar values and norms  
5 | Strongly disagree that people share similar values and norms       

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_0   
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood  get along with each other.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people get along  
2 | Agree that people get along  
3 | Neither agree or disagree that people get along   
4 | Disagree that people get along    
5 | Strongly disagree that people get along        

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_2   
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood  get along with each other.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people get along      
2 | Agree that people get along  
3 | Neither agree or disagree that people get along   
4 | Disagree that people get along     
5 | Strongly disagree that people get along         

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_3   
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood  get along with each other.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people get along     
2 | Agree that people get along  
3 | Neither agree or disagree that people get along    
4 | Disagree that people get along    
5 | Strongly disagree that people get along        

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_4   
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood  get along with each other.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people get along     
2 | Agree that people get along  
3 | Neither agree or disagree that people get along   
4 | Disagree that people get along    
5 | Strongly disagree that people get along         

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Friendly neighbours       
**Variable name**: env_nbs_friend_0     
**Variable description**: Indicator of whether the participant is asked whether members of the area where their live (i.e. their neighbourhood) are friendly/ polite.           
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | People are friendly    
2 | People are somewhat friendly 
3 | People are not really friendly  
4 | People are not friendly    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Belonging to neighbourhood        
**Variable name**: env_nbh_belong_0      
**Variable description**: Indicator of whether the participant asked whether they feel a part of the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Feels part of area     
0 | Does not feel part of area   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Belonging to neighbourhood        
**Variable name**: env_nbh_belong_2      
**Variable description**: Indicator of whether the participant asked whether they feel a part of the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Feels part of area     
0 | Does not feel part of area       

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Belonging to neighbourhood        
**Variable name**: env_nbh_belong_4      
**Variable description**: Indicator of whether the participant asked whether they feel a part of the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Feels part of area     
0 | Does not feel part of area    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_0      
**Variable description**: Indicator of whether the participant agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that they feel lonely   
2 | Agree that they feel lonely
3 | Neither agree or disagree that they feel lonely 
4 | Disagree that they feel lonely  
5 | Strongly disagree that they feel lonely         

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_2      
**Variable description**: Indicator of whether the participant agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that they feel lonely   
2 | Agree that they feel lonely
3 | Neither agree or disagree that they feel lonely 
4 | Disagree that they feel lonely 
5 | Strongly disagree that they feel lonely         

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_3      
**Variable description**: Indicator of whether the participant agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that they feel lonely   
2 | Agree that they feel lonely
3 | Neither agree or disagree that they feel lonely  
4 | Disagree that they feel lonely   
5 | Strongly disagree that they feel lonely        

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_4      
**Variable description**: Indicator of whether the participant agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that they feel lonely   
2 | Agree that they feel lonely
3 | Neither agree or disagree that they feel lonely 
4 | Disagree that they feel lonely  
5 | Strongly disagree that they feel lonely         

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Close-knit community        
**Variable name**: env_nbh_comm_0      
**Variable description**: Members of community in which participant lives is close-knit.  
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |   
2 | 
3 | 
4 |                        
5 |                   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 
# Neighbourhood aesthetics subdomain

### **Variable label**: Neighbourhood cleanliness   
**Variable name**:  env_nbh_clean_0  
**Variable description**:  Indicator of whether the participant perception of the cleanliness (presence of rubbish) of the area where respondent lives (i.e. their neighbourhood).  This variable does not include GLOBE study harmonization and has more answer categories than the dichotomized version.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Area not very clean     
2 | Area not clean   
3 | Area mostly clean   
4 | Area clean             

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood cleanliness   
**Variable name**:  env_nbh_clean_1  
**Variable description**:  Indicator of whether the participant perception of the cleanliness (presence of rubbish) of the area where respondent lives (i.e. their neighbourhood).  This variable does not include GLOBE study harmonization and has more answer categories than the dichotomized version.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Area not very clean     
2 | Area not clean   
3 | Area mostly clean   
4 | Area clean             

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood cleanliness dichotomized     
**Variable name**:  env_nbh_clean_dich_0  
**Variable description**:  Indicator of whether the participant perception of the cleanliness (presence of rubbish) of the area where respondent lives (i.e. their neighbourhood).  This variable includes GLOBE study harmonization.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Area clean             
0 | Area not clean  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood cleanliness dichotomized     
**Variable name**:  env_nbh_clean_dich_1    
**Variable description**:  Indicator of whether the participant perception of the cleanliness (presence of rubbish) of the area where respondent lives (i.e. their neighbourhood).  This variable includes GLOBE study harmonization.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Area clean             
0 | Area not clean  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood cleanliness dichotomized     
**Variable name**:  env_nbh_clean_dich_2    
**Variable description**:  Indicator of whether the participant perception of the cleanliness (presence of rubbish) of the area where respondent lives (i.e. their neighbourhood).  This variable includes GLOBE study harmonization.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Area clean             
0 | Area not clean  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood graffiti and vandalism  
**Variable name**:  env_nbh_gv_0  
**Variable description**:  Respondent perception of graffiti and/or vandalism in  area where respondent lives (i.e. their neighbourhood).  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Graffiti and/or vandalism  
0 | No graffiti and/or vandalism              

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood graffiti and vandalism  
**Variable name**:  env_nbh_gv_2  
**Variable description**:  Respondent perception of graffiti and/or vandalism in  area where respondent lives (i.e. their neighbourhood).  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | No graffiti and/or vandalism   
0 | Graffiti and/or vandalism            

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood noisiness     
**Variable name**:  env_nbh_noisiness_0  
**Variable description**:  Indicator of whether the participant’s perception of presence of excessive noise in their neighbourhood.  Note: there is also a dichotomized version of this variable which includes GLOBE study.      
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Definitely excessive noise      
2 | Some excessive noise    
3 | A little excessive noise    
4 | No excessive noise            

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood noisiness      
**Variable name**:  env_nbh_noisiness_1  
**Variable description**:  Indicator of whether the participant’s perception of presence of excessive noise in their neighbourhood.  Note: there is also a dichotomized version of this variable which includes GLOBE study.         
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Definitely excessive noise      
2 | Some excessive noise    
3 | A little excessive noise    
4 | No excessive noise            

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood noisy    
**Variable name**:  env_nbh_noisy_0  
**Variable description**:  Respondent’s perception of noise in their neighbourhood. Note: GLOBE is included in this dichotomized noise variable, GLOBE does not ask about excessive noise in particular as RECORD and MESA do (it asks: In the past year have you often dealt with: Traffic noise, noise from passing airplanes, street noise, noise from businesses in your neighborhood?).        
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Not noisy         
0 | Noisy        

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood noisy    
**Variable name**:  env_nbh_noisy_1  
**Variable description**:  Respondent’s perception of noise in their neighbourhood. Note: GLOBE is included in this dichotomized noise variable, GLOBE does not ask about excessive noise in particular as RECORD and MESA do (it asks: In the past year have you often dealt with: Traffic noise, noise from passing airplanes, street noise, noise from businesses in your neighborhood?).        
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Not noisy         
0 | Noisy        

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
# Crime & Vandalism subdomain

### **Variable label**: Neighbourhood violence  
**Variable name**: env_nbh_violence_0     
**Variable description**: Respondent’s perception of presence of violence in their neighbourhood.   
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | No violence in neighbourhood
0 | Violence in neighbourhood     

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood violence  
**Variable name**: env_nbh_violence_1     
**Variable description**: Respondent’s perception of presence of violence in their neighbourhood.   
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | No violence in neighbourhood
0 | Violence in neighbourhood     

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood violence  
**Variable name**: env_nbh_violence_2     
**Variable description**: Respondent’s perception of presence of violence in their neighbourhood.   
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | No violence in neighbourhood
0 | Violence in neighbourhood     

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood antisocial and aggressive behaviour 
**Variable name**: env_nbs_anti_0  
**Variable description**: Respondent’s perception of antisocial and aggressive behaviour in their neighbourhood.  
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | No antisocial and aggressive behavior in neighbourhood
0 | Antisocial and aggressive behavior in neighbourhood      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood antisocial and aggressive behaviour 
**Variable name**: env_nbs_anti_1  
**Variable description**: Respondent’s perception of antisocial and aggressive behaviour in their neighbourhood.  
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | No antisocial and aggressive behavior in neighbourhood
0 | Antisocial and aggressive behavior in neighbourhood      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood antisocial and aggressive behaviour 
**Variable name**: env_nbs_anti_2  
**Variable description**: Respondent’s perception of antisocial and aggressive behaviour in their neighbourhood.  
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | No antisocial and aggressive behavior in neighbourhood
0 | Antisocial and aggressive behavior in neighbourhood      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
