---
title: "Perceptions of urban environment DataSchema"
output: html_document
---
# Connecting with Opal data server
## Login to server and assign study data
```{r, echo=FALSE}
#Load R libraries
library(opal)
library(tidyverse)
library(epiDisplay)
library(data.table)
# Create an opal object with the login information
erasmus_opal <- opal.login()
## When you are done with your work, logout of Opal server
# opal.logout(erasmus_opal) 
# Login to Opal server and assign the content of the GLOBE table(s) to your RStudio environment
opal.assign.table.tibble(erasmus_opal, 'GLOBE1991','GLOBE.GLOBE1991', variables = list('v161','v160')) 
GLOBE1991 <- opal.execute(erasmus_opal,'GLOBE1991')

opal.assign.table.tibble(erasmus_opal, 'GLOBE1997','GLOBE.GLOBE1997', variables =list('v14a','v14b'))
GLOBE1997 <- opal.execute(erasmus_opal,'GLOBE1997')

opal.assign.table.tibble(erasmus_opal, 'GLOBE2004','GLOBE.GLOBE2004', variables = list('w069', 'w070','w052','w058','w060','w059','w057','w054','w049','w053','w050','w047','w068','w061','w062')) 
GLOBE2004 <- opal.execute(erasmus_opal,'GLOBE2004')

opal.assign.table.tibble(erasmus_opal, 'GLOBE2011','GLOBE.GLOBE2011', variables = list('v53_d_buur4','v53_c_buur3','v53_a_buur1')) 
GLOBE2011 <- opal.execute(erasmus_opal,'GLOBE2011')

opal.assign.table.tibble(erasmus_opal, 'GLOBE2014','GLOBE.GLOBE2014', variables = list('G14v90_h','G14v90_m','G14v90_j','G14v90_e','G14v90_i','G14v90_f','G14v90_c')) 
GLOBE2014 <- opal.execute(erasmus_opal,'GLOBE2014')
```
## Assign participant id as first column of your harmonized dataframes
```{r,echo=FALSE}
env_GLOBE_0 <- data.frame(id= GLOBE1991$id)
env_GLOBE_1 <- data.frame(id= GLOBE1997$id)
env_GLOBE_2 <- data.frame(id= GLOBE2004$id)
env_GLOBE_3 <- data.frame(id= GLOBE2011$id)
env_GLOBE_4 <- data.frame(id= GLOBE2014$id)
```
# Table of Contents

1. [General neighbourhood safety subdomain](#general-neighbourhood-safety-subdomain)
2. [Social trust subdomain](#social-trust-subdomain)
3. [Social cohesion subdomain](#social-cohesion-subdomain)  
4. [Neighbourhood aesthetics subdomain](#vandalism-subdomain)
5. [Crime and vandalism subdomain](#crime-and-vandalism-subdomain)  

# General neighbourhood safety subdomain  

### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsf_0   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------   
0 |   Does not feel safe at night
1 |   Feels safe at night 

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsf_1   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------   
0 |   Does not feel safe at night 
1 |   Feels safe at night 

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsf_2   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------   
0 |   Does not feel safe at night 
1 |   Feels safe at night 

**Harmonization status**:  complete  
**Harmonization comment**:   The response 'neither agree nor disagree' is collapsed with the negative response 'agree' (I am sometimes afraid to walk...) into the category 'does not feel safe at night', since a neutral response is often chosen due to an individual's reluctance to answer negatively. 	
**R script**:  
```{r, echo=TRUE}
env_GLOBE_2$env_nbh_nsf_2<-recode(as.integer(GLOBE2004$w069),'1'=0L,'2'=0L,'3'=1L)
```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsf_3   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe at night 
1 |   Feels safe at night  


**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsf_4   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe at night 
1 |   Feels safe at night  


**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsf_5   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe at night
1 |   Feels safe at night  
 

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsf_6   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe at night
1 |   Feels safe at night  
  

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_0   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood.        
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe 
1 |   Feels safe 
 

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_1   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood.     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe
1 |   Feels safe 
  

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_2   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood.       
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe 
1 |   Feels safe 
  

**Harmonization status**:  complete
**Harmonization comment**:    Using 2 variables to construct this. If the participant answers “disagree” to both (I am sometimes afraid….) day and night , is coded as “feels safe”, otherwise is coded as unsafe or missing.
**R script**:  
```{r, echo=TRUE}

env_GLOBE_2$env_nbh_sf_2<-ifelse(as.integer(GLOBE2004$w070)<=2 | as.integer(GLOBE2004$w069)<=2,0L,
                                 ifelse(as.integer(GLOBE2004$w070)==3 & as.integer(GLOBE2004$w069)==3,1L,NA))


```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_3   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood.       
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe  
1 |   Feels safe 
 

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_4   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe  
1 |   Feels safe 
 

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_5   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood.       
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe  
1 |   Feels safe 
 

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_6   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood.      
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe 
1 |   Feels safe 
  

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
# Social trust subdomain

### **Variable label**:  Trust in neighbours    
**Variable name**:  env_nbh_trust_0   
**Variable description**:  Indicator of whether the participant agrees that most people in the area where they live (i.e. in their neighbourhood) can be trusted.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People cannot be trusted 
1 | People can be trusted    
        

**Harmonization status**:  impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**:  Trust in neighbours    
**Variable name**:  env_nbh_trust_1   
**Variable description**:  Indicator of whether the participant agrees that most people in the area where they live (i.e. in their neighbourhood) can be trusted.     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People cannot be trusted
1 | People can be trusted    
       

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**:  Trust in neighbours    
**Variable name**:  env_nbh_trust_2     
**Variable description**:  Indicator of whether the participant agrees that most people in the area where they live (i.e. in their neighbourhood) can be trusted.     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People cannot be trusted  
1 | People can be trusted    
    

**Harmonization status**:  complete
**Harmonization comment**:   The response 'neither agree nor disagree' is collapsed with the negative responses 'disagree' and 'strongly disagree' (people...can be trusted) into the category 'people cannot be trusted', since a neutral response is often chosen due to an individual's reluctance to answer negatively.   
**R script**:  
```{r, echo=TRUE}
env_GLOBE_2$env_nbh_trust_2<-recode(as.integer(GLOBE2004$w052),'1'=1L,'2'=1L,'3'=0L,'4'=0L,'5'=0L )

```
### **Variable label**:  Trust in neighbours    
**Variable name**:  env_nbh_trust_3     
**Variable description**:  Indicator of whether the participant agrees that most people in the area where they live (i.e. in their neighbourhood) can be trusted.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People cannot be trusted   
1 | People can be trusted    
   

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**:  Trust in neighbours    
**Variable name**:  env_nbh_trust_4     
**Variable description**:  Indicator of whether the participant agrees that most people in the area where they live (i.e. in their neighbourhood) can be trusted.      
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People cannot be trusted 
1 | People can be trusted    
      

**Harmonization status**:  complete
**Harmonization comment**:   The response 'neither agree nor disagree' is collapsed with the negative responses 'disagree' and 'strongly disagree' (people...can be trusted) into the category 'people cannot be trusted', since a neutral response is often chosen due to an individual's reluctance to answer negatively. 
**R script**:  
```{r, echo=TRUE}
env_GLOBE_4$env_nbh_trust_4<-recode(as.integer(GLOBE2014$G14v90_h),'1'=1L,'2'=1L,'3'=0L,'4'=0L,'5'=0L )
```

### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_among_0   
**Variable description**:  Indicator of whether the participant agrees that there is trust among the people in the area where they live (i.e. in their neighbourhood).    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
------------- | -------------  
0 | People do not trust one another 
1 | People trust one another  


**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**: 
```{r, echo=TRUE}


```
### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_among_1   
**Variable description**:  Indicator of whether the participant agrees that there is trust among the people in the area where they live (i.e. in their neighbourhood).    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
------------- | -------------  
0 | People do not trust one another 
1 | People trust one another 


**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**: 
```{r, echo=TRUE}


```

# Social cohesion subdomain

### **Variable label**: Helpful neighbours  
**Variable name**: env_nbs_help_0  
**Variable description**: Indicator of whether the participant agrees that neighbors would help them if needed, in case of emergency/trouble.  
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Neighbours would not help me
1 | Neighbours would help me   
       

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Helpful neighbours  
**Variable name**: env_nbs_help_1  
**Variable description**: Indicator of whether the participant agrees that neighbors would help them if needed,  in case of emergency/trouble.  
**Value type**: integer   
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Neighbours would not help me  
1 | Neighbours would help me    
       

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Helpful neighbours  
**Variable name**: env_nbs_help_2  
**Variable description**: Indicator of whether the participant agrees that neighbors would help them if needed,  in case of emergency/trouble.  
**Value type**: integer   
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Neighbours would not help me
1 | Neighbours would help me    
         

**Harmonization status**:  complete
**Harmonization comment**:   The response 'neither agree nor disagree' is collapsed with the negative responses 'disagree' and 'strongly disagree' (my neighbours help...) into the category 'neighbours would not help me', since a neutral response is often chosen due to an individual's reluctance to answer negatively. 
**R script**:  
```{r, echo=TRUE}
env_GLOBE_2$env_nbs_help_2<-recode(as.integer(GLOBE2004$w057),'1'=1L,'2'=1L,'3'=0L,'4'=0L,'5'=0L )
```
### **Variable label**: Helpful neighbours  
**Variable name**: env_nbs_help_3    
**Variable description**: Indicator of whether the participant agrees that neighbors would help them if needed,  in case of emergency/trouble.  
**Value type**: integer   
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Neighbours would not help me 
1 | Neighbours would help me    
        

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Helpful neighbours  
**Variable name**: env_nbs_help_4  
**Variable description**: Indicator of whether the participant agrees that neighbors would help them if needed,  in case of emergency/trouble.  
**Value type**: integer   
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Neighbours would not help me  
1 | Neighbours would help me   
    

**Harmonization status**:  complete
**Harmonization comment**:    The response 'neither agree nor disagree' is collapsed with the negative responses 'disagree' and 'strongly disagree' (my neighbours help...) into the category 'neighbours would not help me', since a neutral response is often chosen due to an individual's reluctance to answer negatively. 
**R script**:  
```{r, echo=TRUE}
env_GLOBE_4$env_nbs_help_4<-recode(as.integer(GLOBE2014$G14v90_m),'1'=1L,'2'=1L,'3'=0L,'4'=0L,'5'=0L )

```

### **Variable label**: Cooperating neighbours   
**Variable name**: env_nbs_coop_0   
**Variable description**: Indicator of whether the participant agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out.  
**Value type**: integer  
**Variable unit**: N/A   
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People not willing to help each other  
1 | People willing to help each other   
       

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```

### **Variable label**: Cooperating neighbours    
**Variable name**: env_nbs_coop_1  
**Variable description**: Indicator of whether the participant agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out.    
**Value type**: integer    
**Variable unit**: N/A     
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People not willing to help each other
1 | People willing to help each other   
             

**Harmonization status**:  impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```

### **Variable label**: Cooperating neighbours      
**Variable name**: env_nbs_coop_2  
**Variable description**: Indicator of whether the participant agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out.    
**Value type**: integer    
**Variable unit**: N/A     
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People not willing to help each other  
1 | People willing to help each other   
             

**Harmonization status**:  complete
**Harmonization comment**:  The response 'neither agree nor disagree' is collapsed with the negative responses 'disagree' and 'strongly disagree' (people...help each other) into the category 'people not willing to help each other', since a neutral response is often chosen due to an individual's reluctance to answer negatively. 	 
**R script**:  
```{r, echo=TRUE}
env_GLOBE_2$env_nbs_coop_2<-recode(as.integer(GLOBE2004$w054),'1'=1L,'2'=1L,'3'=0L,'4'=0L,'5'=0L )

```
### **Variable label**: Cooperating neighbours      
**Variable name**: env_nbs_coop_3  
**Variable description**: Indicator of whether the participant agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out.    
**Value type**: integer    
**Variable unit**: N/A     
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People not willing to help each other  
1 | People willing to help each other   
          

**Harmonization status**:  complete
**Harmonization comment**: The response 'neither agree nor disagree' is collapsed with the negative responses 'disagree' and 'strongly disagree' (people...help each other) into the category 'people not willing to help each other', since a neutral response is often chosen due to an individual's reluctance to answer negatively.   
**R script**:  
```{r, echo=TRUE}
env_GLOBE_3$env_nbs_coop_3<-recode(as.integer(GLOBE2011$v53_d_buur4),'1'=1L,'2'=1L,'3'=0L,'4'=0L,'5'=0L)
```  
### **Variable label**: Cooperating neighbours      
**Variable name**: env_nbs_coop_4  
**Variable description**: Indicator of whether the participant agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out.    
**Value type**: integer    
**Variable unit**: N/A     
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People not willing to help each other 
1 | People willing to help each other   
            

**Harmonization status**:  complete
**Harmonization comment**:  The response 'neither agree nor disagree' is collapsed with the negative responses 'disagree' and 'strongly disagree' (people...help each other) into the category 'people not willing to help each other', since a neutral response is often chosen due to an individual's reluctance to answer negatively.  
**R script**:  
```{r, echo=TRUE}
env_GLOBE_4$env_nbs_coop_4<-recode(as.integer(GLOBE2014$G14v90_j),'1'=1L,'2'=1L,'3'=0L,'4'=0L,'5'=0L)

```  

### **Variable label**: Neighbourhood values and norms       
**Variable name**: env_nbh_values_0   
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood share similar values and norms.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people share similar values and norms    
2 | Agree that people share similar values and norms
3 | Neither agree or disagree that people share similar values and norms
4 | Disagree that people share similar values and norms  
5 | Strongly disagree that people share similar values and norms        

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbourhood values and norms       
**Variable name**: env_nbh_values_1     
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood share similar values and norms.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people share similar values and norms    
2 | Agree that people share similar values and norms
3 | Neither agree or disagree that people share similar values and norms
4 | Disagree that people share similar values and norms  
5 | Strongly disagree that people share similar values and norms        

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbourhood values and norms       
**Variable name**: env_nbh_values_2     
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood share similar values and norms.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people share similar values and norms   
2 | Agree that people share similar values and norms
3 | Neither agree or disagree that people share similar values and norms  
4 | Disagree that people share similar values and norms  
5 | Strongly disagree that people share similar values and norms       

**Harmonization status**:  complete
**Harmonization comment**:   no transformation needed since categories match DataSchema categories 
**R script**:  
```{r, echo=TRUE}
env_GLOBE_2$env_nbh_values_2<-recode(as.integer(GLOBE2004$w049),'1'=1L,'2'=2L,'3'=3L,'4'=4L,'5'=5L)

```
### **Variable label**: Neighbourhood values and norms       
**Variable name**: env_nbh_values_3     
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood share similar values and norms.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people share similar values and norms   
2 | Agree that people share similar values and norms
3 | Neither agree or disagree that people share similar values and norms  
4 | Disagree that people share similar values and norms  
5 | Strongly disagree that people share similar values and norms       

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbourhood values and norms       
**Variable name**: env_nbh_values_4     
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood share similar values and norms.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people share similar values and norms   
2 | Agree that people share similar values and norms
3 | Neither agree or disagree that people share similar values and norms 
4 | Disagree that people share similar values and norms  
5 | Strongly disagree that people share similar values and norms       

**Harmonization status**:  complete
**Harmonization comment**:   no transformation needed since categories match DataSchema categories 
**R script**:  
```{r, echo=TRUE}
env_GLOBE_4$env_nbh_values_4<-recode(as.integer(GLOBE2014$G14v90_e),'1'=1L,'2'=2L,'3'=3L,'4'=4L,'5'=5L)
```  
### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_0   
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood  get along with each other.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people get along  
2 | Agree that people get along  
3 | Neither agree or disagree that people get along   
4 | Disagree that people get along    
5 | Strongly disagree that people get along        

**Harmonization status**:  impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_1     
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood  get along with each other.  
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people get along  
2 | Agree that people get along  
3 | Neither agree or disagree that people get along   
4 | Disagree that people get along    
5 | Strongly disagree that people get along        

**Harmonization status**:  impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_2   
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood  get along with each other.   
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people get along      
2 | Agree that people get along  
3 | Neither agree or disagree that people get along   
4 | Disagree that people get along     
5 | Strongly disagree that people get along         

**Harmonization status**:  complete
**Harmonization comment**:   no transformation needed since categories match DataSchema categories 
**R script**:  
```{r, echo=TRUE}
env_GLOBE_2$env_nbs_along_2<-recode(as.integer(GLOBE2004$w053),'1'=1L,'2'=2L,'3'=3L,'4'=4L,'5'=5L)
```
### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_3   
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood  get along with each other.  
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people get along     
2 | Agree that people get along  
3 | Neither agree or disagree that people get along    
4 | Disagree that people get along    
5 | Strongly disagree that people get along        

**Harmonization status**:  complete
**Harmonization comment**:   Original variable was reverse coded to match DataSchema categories.  
**R script**:  
```{r, echo=TRUE}
env_GLOBE_3$env_nbs_along_3<-recode(as.integer(GLOBE2011$v53_c_buur3),'5'=1L,'4'=2L,'3'=3L,'2'=4L,'1'=5L)
```
### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_4   
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood  get along with each other.  
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people get along     
2 | Agree that people get along  
3 | Neither agree or disagree that people get along   
4 | Disagree that people get along    
5 | Strongly disagree that people get along         

**Harmonization status**:  complete
**Harmonization comment**:  no transformation needed since categories match DataSchema categories  
**R script**:  
```{r, echo=TRUE}
env_GLOBE_4$env_nbs_along_4<-recode(as.integer(GLOBE2014$G14v90_i),'1'=1L,'2'=2L,'3'=3L,'4'=4L,'5'=5L)
```
### **Variable label**: Friendly neighbours       
**Variable name**: env_nbs_friendly_0     
**Variable description**: Indicator of whether the participant is asked whether members of the area where their live (i.e. their neighbourhood) are friendly/ polite.           
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | People are friendly    
2 | People are somewhat friendly 
3 | People are not really friendly  
4 | People are not friendly    

**Harmonization status**:  impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Belonging to neighbourhood        
**Variable name**: env_nbh_belong_0        
**Variable description**: Indicator of whether the participant asked whether they feel a part of the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not feel part of area
1 | Feels part of area     
   

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Belonging to neighbourhood        
**Variable name**: env_nbh_belong_1        
**Variable description**: Indicator of whether the participant asked whether they feel a part of the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not feel part of area
1 | Feels part of area     
   

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Belonging to neighbourhood        
**Variable name**: env_nbh_belong_2      
**Variable description**: Indicator of whether the participant asked whether they feel a part of the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not feel part of area  
1 | Feels part of area     
     

**Harmonization status**:  complete
**Harmonization comment**:   The response 'neither agree nor disagree' is collapsed with the negative responses 'disagree' and 'strongly disagree' (I feel at home in neighbourhood) into the category 'does not feel part of area', since a neutral response is often chosen due to an individual's reluctance to answer negatively. 
**R script**:  
```{r, echo=TRUE}
env_GLOBE_2$env_nbh_belong_2<-recode(as.integer(GLOBE2004$w050),'1'=1L,'2'=1L,'3'=0L,'4'=0L,'5'=0L)
```
### **Variable label**: Belonging to neighbourhood        
**Variable name**: env_nbh_belong_3        
**Variable description**: Indicator of whether the participant asked whether they feel a part of the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not feel part of area  
1 | Feels part of area     
     

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Belonging to neighbourhood        
**Variable name**: env_nbh_belong_4      
**Variable description**: Indicator of whether the participant asked whether they feel a part of the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not feel part of area 
1 | Feels part of area     
   

**Harmonization status**:  complete
**Harmonization comment**:   The response 'neither agree nor disagree' is collapsed with the negative responses 'disagree' and 'strongly disagree' (I feel at home in neighbourhood) into the category 'does not feel part of area', since a neutral response is often chosen due to an individual's reluctance to answer negatively.  
**R script**:  
```{r, echo=TRUE}
env_GLOBE_4$env_nbh_belong_4<-recode(as.integer(GLOBE2014$G14v90_f),'1'=1L,'2'=1L,'3'=0L,'4'=0L,'5'=0L)
```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_0      
**Variable description**: Indicator of whether the participant agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that they feel lonely   
2 | Agree that they feel lonely
3 | Neither agree or disagree that they feel lonely 
4 | Disagree that they feel lonely  
5 | Strongly disagree that they feel lonely         

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_1      
**Variable description**: Indicator of whether the participant agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that they feel lonely   
2 | Agree that they feel lonely
3 | Neither agree or disagree that they feel lonely 
4 | Disagree that they feel lonely  
5 | Strongly disagree that they feel lonely         

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_2      
**Variable description**: Indicator of whether the participant agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that they feel lonely   
2 | Agree that they feel lonely
3 | Neither agree or disagree that they feel lonely 
4 | Disagree that they feel lonely 
5 | Strongly disagree that they feel lonely         

**Harmonization status**:  complete
**Harmonization comment**:  no transformation needed since categories match DataSchema categories  
**R script**:  
```{r, echo=TRUE}
env_GLOBE_2$env_nbh_lone_2<-recode(as.integer(GLOBE2004$w047),'1'=1L,'2'=2L,'3'=3L,'4'=4L,'5'=5L)
```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_3      
**Variable description**: Indicator of whether the participant agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that they feel lonely   
2 | Agree that they feel lonely
3 | Neither agree or disagree that they feel lonely  
4 | Disagree that they feel lonely   
5 | Strongly disagree that they feel lonely        

**Harmonization status**:  complete
**Harmonization comment**: Original variable was reverse coded to match DataSchema categories.    
**R script**:  
```{r, echo=TRUE}
env_GLOBE_3$env_nbh_lone_3<-recode(as.integer(GLOBE2011$v53_a_buur1),'1'=5L,'2'=4L,'3'=3L,'4'=2L,'5'=1L)
```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_4      
**Variable description**: Indicator of whether the participant agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that they feel lonely   
2 | Agree that they feel lonely
3 | Neither agree or disagree that they feel lonely 
4 | Disagree that they feel lonely  
5 | Strongly disagree that they feel lonely         

**Harmonization status**:  complete
**Harmonization comment**:   no transformation needed since categories match DataSchema categories 
**R script**:  
```{r, echo=TRUE}
env_GLOBE_4$env_nbh_lone_4<-recode(as.integer(GLOBE2014$G14v90_c),'1'=1L,'2'=2L,'3'=3L,'4'=4L,'5'=5L)
```  
### **Variable label**: Close-knit community        
**Variable name**: env_nbh_comm_0      
**Variable description**: Indicator of whether the participant agrees that members of the area in which participant lives are close-knit (community solidarity).
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strong neighbourhood solidarity     
2 | Some neighbourhood solidarity    
3 | A little neighbourhood solidarity    
4 | No neighbourhood solidarity                   

**Harmonization status**:  impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


``` 
### **Variable label**: Close-knit community        
**Variable name**: env_nbh_comm_1      
**Variable description**: Indicator of whether the participant agrees that members of the area in which participant lives are close-knit (community solidarity).
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strong neighbourhood solidarity     
2 | Some neighbourhood solidarity    
3 | A little neighbourhood solidarity    
4 | No neighbourhood solidarity                   

**Harmonization status**:   impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Close-knit community        
**Variable name**: env_nbh_comm_2      
**Variable description**: Indicator of whether the participant agrees that members of the area in which participant lives are close-knit (community solidarity).
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strong neighbourhood solidarity     
2 | Some neighbourhood solidarity    
3 | A little neighbourhood solidarity    
4 | No neighbourhood solidarity                   

**Harmonization status**:   impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Close-knit community        
**Variable name**: env_nbh_comm_3      
**Variable description**: Indicator of whether the participant agrees that members of the area in which participant lives are close-knit (community solidarity).
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strong neighbourhood solidarity     
2 | Some neighbourhood solidarity    
3 | A little neighbourhood solidarity    
4 | No neighbourhood solidarity                   

**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Close-knit community        
**Variable name**: env_nbh_comm_4      
**Variable description**: Indicator of whether the participant agrees that members of the area in which participant lives are close-knit (community solidarity).
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strong neighbourhood solidarity     
2 | Some neighbourhood solidarity    
3 | A little neighbourhood solidarity    
4 | No neighbourhood solidarity                   

**Harmonization status**:   impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}


```
# Neighbourhood aesthetics subdomain

### **Variable label**: Neighbourhood cleanliness (4-level)   
**Variable name**:  env_nbh_clean_0  
**Variable description**:  Indicator of the participant's perception of the cleanliness (presence of rubbish) of the area where the respondent lives (i.e. their neighbourhood).      
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Area not very clean     
2 | Area not clean   
3 | Area mostly clean   
4 | Area clean             

**Harmonization status**:  impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbourhood cleanliness (4-level)     
**Variable name**:  env_nbh_clean_1  
**Variable description**:  Indicator of the participant's perception of the cleanliness (presence of rubbish) of the area where the respondent lives (i.e. their neighbourhood).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Area not very clean     
2 | Area not clean   
3 | Area mostly clean   
4 | Area clean             

**Harmonization status**:  impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbourhood cleanliness (2-level)       
**Variable name**:  env_nbh_clean_dich_0  
**Variable description**:  Indicator of the participant's perception of the cleanliness (presence of rubbish) of the area where the respondent lives (i.e. their neighbourhood).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Area not clean  
1 | Area clean             


**Harmonization status**:  impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbourhood cleanliness (2-level)       
**Variable name**:  env_nbh_clean_dich_1    
**Variable description**:  Indicator of the participant's perception of the cleanliness (presence of rubbish) of the area where the respondent lives (i.e. their neighbourhood).   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Area not clean 
1 | Area clean             
 

**Harmonization status**:  impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbourhood cleanliness (2-level)      
**Variable name**:  env_nbh_clean_dich_2    
**Variable description**:  Indicator of the participant's perception of the cleanliness (presence of rubbish) of the area where the respondent lives (i.e. their neighbourhood).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Area not clean 
1 | Area clean             
 

**Harmonization status**:  complete 
**Harmonization comment**:   category 2, 'sometimes' (how often does litter occur in your neighbourhood) is recoded as area not clean for the DataSchema.  
**R script**:  
```{r, echo=TRUE}
env_GLOBE_2$env_nbh_clean_dich_2<-recode(as.integer(GLOBE2004$w058),'1'=0L,'2'=0L,'3'=1L)
table(env_GLOBE_2$env_nbh_clean_dich_2)
```

### **Variable label**: Neighbourhood noisiness (4-level)       
**Variable name**:  env_nbh_noise_0  
**Variable description**:  Indicator of the participant's perception of presence of excessive noise in their neighbourhood.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Definitely excessive noise      
2 | Some excessive noise    
3 | A little excessive noise    
4 | No excessive noise            

**Harmonization status**:  impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbourhood noisiness (4-level)       
**Variable name**:  env_nbh_noise_1  
**Variable description**:  Indicator of the participant's perception of presence of excessive noise in their neighbourhood.     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Definitely excessive noise      
2 | Some excessive noise    
3 | A little excessive noise    
4 | No excessive noise            

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbourhood noisiness (2-level)       
**Variable name**:  env_nbh_noise_dich_0    
**Variable description**:  Indicator of the participant's perception of presence of excessive noise in their neighbourhood, dichotomized.       
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Noisy 
1 | Not noisy         
       

**Harmonization status**:  complete
**Harmonization comment**: GLOBE variable asks about noise nuisance in particular and is also binary.    
**R script**:  
```{r, echo=TRUE}
env_GLOBE_0$env_nbh_noise_dich_0<-recode(as.integer(GLOBE1991$v160),'1'=0L,'2'=1L)
```
### **Variable label**: Neighbourhood noisiness (2-level)     
**Variable name**:  env_nbh_noise_dich_1  
**Variable description**:  Indicator of the participant's perception of presence of excessive noise in their neighbourhood, dichotomized.          
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Noisy  
1 | Not noisy         
      

**Harmonization status**:  complete
**Harmonization comment**:  GLOBE variable asks about noise nuisance in particular and is also binary.    
**R script**:  
```{r, echo=TRUE}
env_GLOBE_1$env_nbh_noise_dich_1<-recode(as.integer(GLOBE1997$v14a),'1'=0L,'2'=1L)
```
### **Variable label**: Neighbourhood traffic noise     
**Variable name**:  env_nbh_traf_noise_0    
**Variable description**:  Indicator of  the participant's perception of presence of noise from traffic, in their neighbourhood.            
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Traffic noise 
1 | No traffic noise          
       

**Harmonization status**:  complete
**Harmonization comment**: GLOBE variable asks in particular regarding the past 12 months, has respondent dealt with: traffic noise, noise from passing airplanes, street noise, noise from businesses in  neighbourhood? and variable is also binary.  
**R script**:  
```{r, echo=TRUE}
env_GLOBE_0$env_nbh_traf_noise_0<-recode(as.integer(GLOBE1991$v161),'1'=0L,'2'=1L)
```
### **Variable label**: Neighbourhood traffic noise    
**Variable name**:  env_nbh_traf_noise_1  
**Variable description**:  Indicator of  the participant's perception of presence of noise from traffic, in their neighbourhood.            
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Traffic noise 
1 | No traffic noise         
      

**Harmonization status**:  complete
**Harmonization comment**: GLOBE variable asks in particular regarding the past 12 months, has respondent dealt with: traffic noise, noise from passing airplanes, street noise, noise from businesses in  neighbourhood? and variable is also binary.  
**R script**:   
```{r, echo=TRUE}
env_GLOBE_1$env_nbh_traf_noise_1<-recode(as.integer(GLOBE1997$v14b),'1'=0L,'2'=1L)
```
# Crime and vandalism subdomain

### **Variable label**: Neighbourhood violence  
**Variable name**: env_nbh_violence_0     
**Variable description**:  Indicator of the participant's perception of violence in their neighbourhood.  
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Violence in neighbourhood  
1 | No violence in neighbourhood
   

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbourhood violence  
**Variable name**: env_nbh_violence_1     
**Variable description**: Indicator of the participant's perception of violence in their neighbourhood.       
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Violence in neighbourhood
1 | No violence in neighbourhood
     

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbourhood violence  
**Variable name**: env_nbh_violence_2     
**Variable description**: Indicator of the participant's perception of violence in their neighbourhood.      
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Violence in neighbourhood  
1 | No violence in neighbourhood
   

**Harmonization status**:  complete
**Harmonization comment**:   category 2 response 'sometimes' (... crimes of violence occur) is coded as 'violence in the neighbourhood'
**R script**:  
```{r, echo=TRUE}
env_GLOBE_2$env_nbh_violence_2<-recode(as.integer(GLOBE2004$w068),'1'=0L,'2'=0L,'3'=1L)
```
### **Variable label**: Neighbourhood antisocial and aggressive behaviour 
**Variable name**: env_nbs_anti_0  
**Variable description**: Indicator of the participant's perception of antisocial and aggressive behaviour in their neighbourhood.    
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Antisocial and aggressive behavior in neighbourhood 
1 | No antisocial and aggressive behavior in neighbourhood
     

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbourhood antisocial and aggressive behaviour 
**Variable name**: env_nbs_anti_1  
**Variable description**: Indicator of the participant's perception of antisocial and aggressive behaviour in their neighbourhood.   
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Antisocial and aggressive behavior in neighbourhood 
1 | No antisocial and aggressive behavior in neighbourhood
     

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbourhood antisocial and aggressive behaviour 
**Variable name**: env_nbs_anti_2  
**Variable description**: Indicator of the participant's perception of antisocial and aggressive behaviour in their neighbourhood.    
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Antisocial and aggressive behavior in neighbourhood  
1 | No antisocial and aggressive behavior in neighbourhood
    

**Harmonization status**:  complete
**Harmonization comment**:   category 2 response 'sometimes' (... youth nuisance occurs) is coded as 'antisocial and aggressive behavior in neighbourhood'; GLOBE asks about youth nuisance in particular
**R script**:  
```{r, echo=TRUE}
env_GLOBE_2$env_nbs_anti_2<-recode(as.integer(GLOBE2004$w061),'1'=0L,'2'=0L,'3'=1L)
```
### **Variable label**: Neighbourhood graffiti and vandalism  
**Variable name**:  env_nbh_gv_0  
**Variable description**:  Indicator of the participant's perception of graffiti and/or vandalism in the area where the respondent lives (i.e. their neighbourhood).    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | No graffiti and no vandalism 
1 | Graffiti and/or vandalism  
             

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbourhood graffiti and vandalism  
**Variable name**:  env_nbh_gv_1    
**Variable description**:  Indicator of the participant's perception of graffiti and/or vandalism in the area where the respondent lives (i.e. their neighbourhood).   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | No graffiti and no vandalism 
1 | Graffiti and no vandalism  
             

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbourhood graffiti and vandalism    
**Variable name**:  env_nbh_gv_2  
**Variable description**:  Indicator of the participant's perception of graffiti and/or vandalism in the area where the respondent lives (i.e. their neighbourhood).   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | No graffiti and no vandalism 
1 | Graffiti and/or vandalism  
           

**Harmonization status**:  complete
**Harmonization comment**:  composite variable from 2 items asking separately about graffiti and vandalism; category 2 response 'sometimes' (... vandalism/ graffiti occurs) is coded 'Graffiti and/or vandalism'. Presence of at least graffiti or vandalism, or both, is coded as 1, thus a NA on one of the variables plus a 1 on the other is coded as a 1. A 0 response on one variable and a NA on the other variable is coded as NA. 
**R script**:  
```{r, echo=TRUE}
GLOBE2004$w060<-recode(as.integer(GLOBE2004$w060),'1'=1L,'2'=1L,'3'=0L)
GLOBE2004$w059<-recode(as.integer(GLOBE2004$w059),'1'=1L,'2'=1L,'3'=0L)

env_GLOBE_2$env_nbh_gv_2<- ifelse((GLOBE2004$w060 == 0 & GLOBE2004$w059 == 0), 0, 
      (ifelse (GLOBE2004$w060 == 1 | GLOBE2004$w059 == 1, 1, NA)))

```
### **Variable label**: Theft of transportation method   
**Variable name**: env_nbh_theft_0     
**Variable description**:  Indicator of the participant's perception of the occurrence of theft of transport vehicle in their neighbourhood.  
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Theft of vehicle in neighbourhood  
1 | No theft of vehicle in neighbourhood


**Harmonization status**:  impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Theft of transportation method   
**Variable name**: env_nbh_theft_1     
**Variable description**: Indicator of the participant's perception of the occurrence of theft of transport vehicle in their neighbourhood.         
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Theft of vehicle in neighbourhood  
1 | No theft of vehicle in neighbourhood
     

**Harmonization status**:  impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Theft of transportation method   
**Variable name**: env_nbh_theft_2     
**Variable description**: Indicator of the participant's perception of the occurrence of theft of transport vehicle in their neighbourhood.        
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Theft of vehicle in neighbourhood  
1 | No theft of vehicle in neighbourhood


**Harmonization status**:  complete
**Harmonization comment**:   GLOBE asks about bicycle theft, RECORD asks about vehicle theft. Category 2, 'sometimes' (bicycle theft occurs in the neighbourhood) is coded as there if theft in the neighbourhood 
**R script**: 
```{r, echo=TRUE}
env_GLOBE_2$env_nbh_theft_2<-recode(as.integer(GLOBE2004$w062),'1'=0L,'2'=0L,'3'=1L)

```
