---
title: "Perceptions of urban environment DataSchema"
output: html_document
---
# Table of Contents
1. [General neighborhood safety subdomain](#general-neighborhood-safety-subdomain)
2. [Social trust subdomain](#social-trust-subdomain)
3. [Crime subdomain](#crime-subdomain)
4. [Vandalism subdomain](#vandalism-subdomain)
5. [Social cohesion subdomain](#social-cohesion-subdomain)
6. [Index of deprivation subdomain](#index-of-deprivation-subdomain)

# General neighborhood safety subdomain

### **Variable label**:   
**Variable name**:   
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Social trust subdomain

### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_0   
**Variable description**:  Respondent is asked if most people in the area where they live  (i.e. in their neighbourhood)  can be trusted  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | yes    
0 | no     
999 | missing   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_1   
**Variable description**:  Respondent is asked if most people in the area where they live  (i.e. in their neighbourhood)  can be trusted  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | yes    
0 | no     
999 | missing   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Crime subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Vandalism subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Social cohesion subdomain

### **Variable label**: Helpful neighbours  
**Variable name**: env_nbhs_help_0  
**Variable description**: Respondent agrees that neighbors would help them if needed, in case of emergency/trouble  
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | yes    
0 | no     
999 | missing  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Helpful neighbours  
**Variable name**: env_nbhs_help_1  
**Variable description**: Respondent agrees that neighbors would help them if needed,  in case of emergency/trouble  
**Value type**: integer   
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | yes    
0 | no     
999 | missing  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```


### **Variable label**: Neighbours cooperate  
**Variable name**: env_nbhs_coop_0   
**Variable description**: Respondent agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out  
**Value type**: integer  
**Variable unit**: N/A   
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | yes    
0 | no     
999 | missing    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Neighbours cooperate    
**Variable name**: env_nbhs_coop_1  
**Variable description**: Respondent agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out    
**Value type**: integer    
**Variable unit**: N/A     
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | yes    
0 | no     
999 | missing      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Neighbours cooperate    
**Variable name**: env_nbhs_coop_2  
**Variable description**: Respondent agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out    
**Value type**: integer    
**Variable unit**: N/A     
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | yes    
0 | no     
999 | missing      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Neighbourhood values and norms       
**Variable name**: env_nbh_values_0   
**Variable description**: Respondent asked if they agree that people in their neighbourhood share similar values and norms        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree    
2 | Agree 
3 | Neither agree or disagree  
4 | Disagree   
5 | Strongly disagree   
999 | missing      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Neighbourhood values and norms       
**Variable name**: env_nbh_values_1   
**Variable description**: Respondent asked if they agree that people in their neighbourhood share similar values and norms        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree    
2 | Agree 
3 | Neither agree or disagree  
4 | Disagree   
5 | Strongly disagree   
999 | missing      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbours get along       
**Variable name**: env_nbhs_along_0   
**Variable description**: Respondent  asked whether they agree that people in their neighbourhood  get along with each other        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree    
2 | Agree 
3 | Neither agree or disagree  
4 | Disagree   
5 | Strongly disagree   
999 | missing      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbours get along       
**Variable name**: env_nbhs_along_1   
**Variable description**: Respondent  asked whether they agree that people in their neighbourhood  get along with each other        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree    
2 | Agree 
3 | Neither agree or disagree  
4 | Disagree   
5 | Strongly disagree   
999 | missing      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbours get along       
**Variable name**: env_nbhs_along_2   
**Variable description**: Respondent  asked whether they agree that people in their neighbourhood  get along with each other        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree    
2 | Agree 
3 | Neither agree or disagree  
4 | Disagree   
5 | Strongly disagree   
999 | missing      

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbours are friendly       
**Variable name**: env_nbhs_friend_0     
**Variable description**: Respondent is asked whether members of the area where their live (i.e. their neighbourhood) are friendly/ polite           
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Friendly    
2 | Somewhat friendly 
3 | Not really friendly  
4 | Not friendly    
999 | missing  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Belonging to neighbourhood        
**Variable name**: env_nbh_belong_0      
**Variable description**: Respondent is asked whether they feel like they belong / feel a part of,  the area where they live (i.e. their community, their neighbourhood)  
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Yes    
0 | No   
999 | missing  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Belonging to neighbourhood        
**Variable name**: env_nbh_belong_1      
**Variable description**: Respondent is asked whether they feel like they belong / feel a part of,  the area where they live (i.e. their community, their neighbourhood)  
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Yes    
0 | No   
999 | missing  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
# Index of deprivation subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
