---
title: "Perceptions of urban environment DataSchema"
output: html_document
---
```{r, echo=TRUE}
library(tidyverse)
library(epiDisplay)
library(scales) 
library(car)
# Connecting with Opal data server
## Login to server and assign study data
#Load Opal R library
library(opal)
# Create an opal object with the login information
erasmus_opal <- opal.login()
#Login to Opal server and assign the content of the LASA table(s) to your RStudio environment
# CLSA-cop_0
opal.assign.table.tibble(erasmus_opal, 'CoP4_Baseline', 'CLSA_1.CoP4_Baseline', variables = list('ENV_PPLTRST_MCQ','ENV_PPLHLP_MCQ','ENV_PPLFRNDLY_MCQ','ENV_FLLNLY_MCQ','ENV_CLEAN_MCQ','ENV_HMPRB_NOI_MCQ','ENV_VNDLSM_MCQ'))
CoP4_Baseline <- opal.execute(erasmus_opal,'CoP4_Baseline')
# CLSA-cop_1
opal.assign.table.tibble(erasmus_opal, 'CoP_FU1', 'CLSA_1.CoP_FU1', variables = list('ENV_PPLTRST_COF1','ENV_PPLHLP_COF1','ENV_PPLFRNDLY_COF1','ENV_FLLNLY_COF1','ENV_CLEAN_COF1','ENV_HMPRB_NOI_COF1','ENV_VNDLSM_COF1','SPA_COHES_COF1'))
CoP_FU1 <- opal.execute(erasmus_opal,'CoP_FU1')
```
## Assign participant id as first column of your harmonized dataframes
```{r, echo=FALSE}
soc_CLSA_cop_0 <- data.frame(id = CoP4_Baseline$id)
soc_CLSA_cop_1 <- data.frame(id = CoP_FU1$id)
# When you are done with your work, logout of Opal server
opal.logout(erasmus_opal)
```
# Table of Contents

1. [General neighborhood safety subdomain](#general-neighborhood-safety-subdomain)
2. [Social trust subdomain](#social-trust-subdomain)
3. [Social cohesion subdomain](#social-cohesion-subdomain)  
4. [Neighbourhood aesthetics subdomain](#vandalism-subdomain)
5. [Crime and vandalism subdomain](#crime-and-vandalism-subdomain)  

# General neighborhood safety subdomain

### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsf_0   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------   
0 |   Does not feel safe at night
1 |   Feels safe at night 

**Harmonization status**:   impossible     
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsf_1   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------   
0 |   Does not feel safe at night 
1 |   Feels safe at night 

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsf_2   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------   
0 |   Does not feel safe at night 
1 |   Feels safe at night 

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsf_3   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe at night 
1 |   Feels safe at night  


**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsf_4   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe at night 
1 |   Feels safe at night  


**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsf_5   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe at night
1 |   Feels safe at night  
 

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe at night     
**Variable name**: env_nbh_nsf_6   
**Variable description**:  Indicator of whether the participant agrees that they feel safe at night in the area where they live (i.e. their neighbourhood).   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe at night
1 |   Feels safe at night  
  

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_0   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood.        
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe 
1 |   Feels safe 
 

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_1   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood.     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe
1 |   Feels safe 
  

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_2   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood.       
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe 
1 |   Feels safe 
  

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_3   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood.       
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe  
1 |   Feels safe 
 

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_4   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe  
1 |   Feels safe 
 

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_5   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood.       
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe  
1 |   Feels safe 
 

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Feels safe in neighbourhood     
**Variable name**: env_nbh_sf_6   
**Variable description**:  Indicator of whether the participant agrees that they feel safe in their neighbourhood.      
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel safe 
1 |   Feels safe 
  

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
# Social trust subdomain

### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_0   
**Variable description**:  Indicator of whether the participant agrees that most people in the area where they live (i.e. in their neighbourhood) can be trusted.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People cannot be trusted 
1 | People can be trusted    
        

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(CoP4_Baseline$ENV_PPLTRST_MCQ, useNA="always") 

soc_CLSA_cop_0$env_nbh_trust_0 <- ifelse(CoP4_Baseline$ENV_PPLTRST_MCQ ==1 | CoP4_Baseline$ENV_PPLTRST_MCQ ==2,1L, 
                                           ifelse(CoP4_Baseline$ENV_PPLTRST_MCQ ==3 | CoP4_Baseline$ENV_PPLTRST_MCQ ==4,0L,NA))

table(soc_CLSA_cop_0$env_nbh_trust_0, useNA="always") 
```
### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_1   
**Variable description**:  Indicator of whether the participant agrees that most people in the area where they live (i.e. in their neighbourhood) can be trusted.     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People cannot be trusted
1 | People can be trusted    
       

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(CoP_FU1$ENV_PPLTRST_COF1, useNA="always") 

soc_CLSA_cop_1$env_nbh_trust_1 <- ifelse(CoP_FU1$ENV_PPLTRST_COF1 ==1 | CoP_FU1$ENV_PPLTRST_COF1 ==2,1L, 
                                           ifelse(CoP_FU1$ENV_PPLTRST_COF1 ==3 | CoP_FU1$ENV_PPLTRST_COF1 ==4,0L,NA))

table(soc_CLSA_cop_1$env_nbh_trust_1, useNA="always") 
```
### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_2     
**Variable description**:  Indicator of whether the participant agrees that most people in the area where they live (i.e. in their neighbourhood) can be trusted.     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People cannot be trusted  
1 | People can be trusted    
    

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_3     
**Variable description**:  Indicator of whether the participant agrees that most people in the area where they live (i.e. in their neighbourhood) can be trusted.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People cannot be trusted   
1 | People can be trusted    
   

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_4     
**Variable description**:  Indicator of whether the participant agrees that most people in the area where they live (i.e. in their neighbourhood) can be trusted.     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People cannot be trusted 
1 | People can be trusted    
      

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_among_0   
**Variable description**:  Indicator of whether the participant agrees that there is trust among the people in the area where they live (i.e. in their neighbourhood).    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
------------- | -------------  
0 | People do not trust one another 
1 | People trust one another  


**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**: 
```{r, echo=TRUE}


```
### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_among_1   
**Variable description**:  Indicator of whether the participant agrees that there is trust among the people in the area where they live (i.e. in their neighbourhood).    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
------------- | -------------  
0 | People do not trust one another 
1 | People trust one another 


**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**: 
```{r, echo=TRUE}


```
### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_among_0   
**Variable description**:  Indicator of whether the participant agrees that there is trust among the people in the area where they live (i.e. in their neighbourhood).    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
------------- | -------------  
0 | People do not trust one another 
1 | People trust one another  


**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**: 
```{r, echo=TRUE}


```
### **Variable label**:  Neighbourhood  trust  
**Variable name**:  env_nbh_trust_among_1   
**Variable description**:  Indicator of whether the participant agrees that there is trust among the people in the area where they live (i.e. in their neighbourhood).    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
------------- | -------------  
0 | People do not trust one another 
1 | People trust one another 


**Harmonization status**:   impossible 
**Harmonization comment**:   
**R script**: 
```{r, echo=TRUE}


```

# Social cohesion subdomain

### **Variable label**: Helpful neighbours  
**Variable name**: env_nbs_help_0  
**Variable description**: Indicator of whether the participant agrees that neighbors would help them if needed, in case of emergency/trouble.  
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Neighbours would not help me
1 | Neighbours would help me   
       

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Helpful neighbours  
**Variable name**: env_nbs_help_1  
**Variable description**: Indicator of whether the participant agrees that neighbors would help them if needed,  in case of emergency/trouble.  
**Value type**: integer   
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Neighbours would not help me  
1 | Neighbours would help me    
       

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Helpful neighbours  
**Variable name**: env_nbs_help_2  
**Variable description**: Indicator of whether the participant agrees that neighbors would help them if needed,  in case of emergency/trouble.  
**Value type**: integer   
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Neighbours would not help me
1 | Neighbours would help me    
         

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Helpful neighbours  
**Variable name**: env_nbs_help_3    
**Variable description**: Indicator of whether the participant agrees that neighbors would help them if needed,  in case of emergency/trouble.  
**Value type**: integer   
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Neighbours would not help me 
1 | Neighbours would help me    
        

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Helpful neighbours  
**Variable name**: env_nbs_help_4  
**Variable description**: Indicator of whether the participant agrees that neighbors would help them if needed,  in case of emergency/trouble.  
**Value type**: integer   
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Neighbours would not help me  
1 | Neighbours would help me   
    

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Neighbours cooperate  
**Variable name**: env_nbs_coop_0   
**Variable description**: Indicator of whether the participant agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out.  
**Value type**: integer  
**Variable unit**: N/A   
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People not willing to help each other  
1 | People willing to help each other   
       

**Harmonization status**:  complete  
**Harmonization comment**:  Study specific items asks: Lots of people in local area who would help if in trouble.
**R script**:  
```{r, echo=TRUE}
table(CoP4_Baseline$ENV_PPLHLP_MCQ, useNA="always") 

soc_CLSA_cop_0$env_nbs_coop_0 <- ifelse(CoP4_Baseline$ENV_PPLHLP_MCQ ==1 |CoP4_Baseline$ENV_PPLHLP_MCQ ==2,1L, 
                                           ifelse(CoP4_Baseline$ENV_PPLHLP_MCQ ==3 |CoP4_Baseline$ENV_PPLHLP_MCQ ==4,0L,NA))

table(soc_CLSA_cop_0$env_nbs_coop_0, useNA="always") 

```

### **Variable label**: Cooperating neighbours    
**Variable name**: env_nbs_coop_1  
**Variable description**: Indicator of whether the participant agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out.    
**Value type**: integer    
**Variable unit**: N/A     
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People not willing to help each other
1 | People willing to help each other   
             

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(CoP_FU1$ENV_PPLHLP_COF1, useNA="always") 

soc_CLSA_cop_1$env_nbs_coop_1 <- ifelse(CoP_FU1$ENV_PPLHLP_COF1 ==1 |CoP_FU1$ENV_PPLHLP_COF1 ==2,1L, 
                                           ifelse(CoP_FU1$ENV_PPLHLP_COF1 ==3 |CoP_FU1$ENV_PPLHLP_COF1 ==4,0L,NA))

table(soc_CLSA_cop_1$env_nbs_coop_1, useNA="always") 
```

### **Variable label**: Cooperating neighbours      
**Variable name**: env_nbs_coop_2  
**Variable description**: Indicator of whether the participant agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out.    
**Value type**: integer    
**Variable unit**: N/A     
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People not willing to help each other  
1 | People willing to help each other   
             

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Cooperating neighbours      
**Variable name**: env_nbs_coop_3  
**Variable description**: Indicator of whether the participant agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out.    
**Value type**: integer    
**Variable unit**: N/A     
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People not willing to help each other  
1 | People willing to help each other   
          

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Cooperating neighbours      
**Variable name**: env_nbs_coop_4  
**Variable description**: Indicator of whether the participant agrees that members of the area where they live (i.e. their community or their neighbourhood) help each other out.    
**Value type**: integer    
**Variable unit**: N/A     
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | People not willing to help each other 
1 | People willing to help each other   
            

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Neighbourhood values and norms       
**Variable name**: env_nbh_values_0   
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood share similar values and norms.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people share similar values and norms    
2 | Agree that people share similar values and norms
3 | Neither agree or disagree that people share similar values and norms
4 | Disagree that people share similar values and norms  
5 | Strongly disagree that people share similar values and norms        

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood values and norms       
**Variable name**: env_nbh_values_1     
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood share similar values and norms.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people share similar values and norms    
2 | Agree that people share similar values and norms
3 | Neither agree or disagree that people share similar values and norms
4 | Disagree that people share similar values and norms  
5 | Strongly disagree that people share similar values and norms        

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood values and norms       
**Variable name**: env_nbh_values_2     
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood share similar values and norms.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people share similar values and norms   
2 | Agree that people share similar values and norms
3 | Neither agree or disagree that people share similar values and norms  
4 | Disagree that people share similar values and norms  
5 | Strongly disagree that people share similar values and norms       

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood values and norms       
**Variable name**: env_nbh_values_3     
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood share similar values and norms.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people share similar values and norms   
2 | Agree that people share similar values and norms
3 | Neither agree or disagree that people share similar values and norms  
4 | Disagree that people share similar values and norms  
5 | Strongly disagree that people share similar values and norms       

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood values and norms       
**Variable name**: env_nbh_values_4     
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood share similar values and norms.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people share similar values and norms   
2 | Agree that people share similar values and norms
3 | Neither agree or disagree that people share similar values and norms 
4 | Disagree that people share similar values and norms  
5 | Strongly disagree that people share similar values and norms       

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_0   
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood  get along with each other.        
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people get along  
2 | Agree that people get along  
3 | Neither agree or disagree that people get along   
4 | Disagree that people get along    
5 | Strongly disagree that people get along        

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_1     
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood  get along with each other.  
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people get along  
2 | Agree that people get along  
3 | Neither agree or disagree that people get along   
4 | Disagree that people get along    
5 | Strongly disagree that people get along        

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_2   
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood  get along with each other.   
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people get along      
2 | Agree that people get along  
3 | Neither agree or disagree that people get along   
4 | Disagree that people get along     
5 | Strongly disagree that people get along         

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_3   
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood  get along with each other.  
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people get along     
2 | Agree that people get along  
3 | Neither agree or disagree that people get along    
4 | Disagree that people get along    
5 | Strongly disagree that people get along        

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbours get along       
**Variable name**: env_nbs_along_4   
**Variable description**: Indicator of whether the participant agrees that people in their neighbourhood  get along with each other.  
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that people get along     
2 | Agree that people get along  
3 | Neither agree or disagree that people get along   
4 | Disagree that people get along    
5 | Strongly disagree that people get along         

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Friendly neighbours       
**Variable name**: env_nbs_friendly_0     
**Variable description**: Indicator of whether the participant is asked whether members of the area where their live (i.e. their neighbourhood) are friendly/ polite.           
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | People are friendly    
2 | People are somewhat friendly 
3 | People are not really friendly  
4 | People are not friendly    

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(CoP4_Baseline$ENV_PPLFRNDLY_MCQ, useNA="always") 

soc_CLSA_cop_0$env_nbs_friendly_0 <- ifelse(CoP4_Baseline$ENV_PPLFRNDLY_MCQ ==1,1L, 
                                           ifelse(CoP4_Baseline$ENV_PPLFRNDLY_MCQ==2,2L,
                                            ifelse(CoP4_Baseline$ENV_PPLFRNDLY_MCQ==3,3L,
                                                   ifelse(CoP4_Baseline$ENV_PPLFRNDLY_MCQ==4,4L,NA))))

table(soc_CLSA_cop_0$env_nbs_friendly_0, useNA="always") 
```
### **Variable label**: Belonging to neighbourhood        
**Variable name**: env_nbh_belong_0        
**Variable description**: Indicator of whether the participant asked whether they feel a part of the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not feel part of area
1 | Feels part of area     
   

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#not collected at baseline

```
### **Variable label**: Belonging to neighbourhood        
**Variable name**: env_nbh_belong_1        
**Variable description**: Indicator of whether the participant asked whether they feel a part of the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not feel part of area
1 | Feels part of area     
   

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

# per Paraminder, PI, use this not ENV_FLPRTAREA_MCQ
table(CoP_FU1$SPA_COHES_COF1, useNA="always") 

soc_CLSA_cop_1$env_nbh_belong_1 <- ifelse(CoP_FU1$SPA_COHES_COF1 ==1 | CoP_FU1$SPA_COHES_COF1==2,1L, 
                                            ifelse(CoP_FU1$SPA_COHES_COF1==3 | CoP_FU1$SPA_COHES_COF1==4,0L,NA))

table(soc_CLSA_cop_1$env_nbh_belong_1, useNA="always") 
```
### **Variable label**: Belonging to neighbourhood        
**Variable name**: env_nbh_belong_2      
**Variable description**: Indicator of whether the participant asked whether they feel a part of the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not feel part of area  
1 | Feels part of area     
     

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Belonging to neighbourhood        
**Variable name**: env_nbh_belong_3        
**Variable description**: Indicator of whether the participant asked whether they feel a part of the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not feel part of area  
1 | Feels part of area     
     

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Belonging to neighbourhood        
**Variable name**: env_nbh_belong_4      
**Variable description**: Indicator of whether the participant asked whether they feel a part of the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not feel part of area 
1 | Feels part of area     
   

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_0      
**Variable description**: Indicator of whether the participant agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that they feel lonely   
2 | Agree that they feel lonely
3 | Neither agree or disagree that they feel lonely 
4 | Disagree that they feel lonely  
5 | Strongly disagree that they feel lonely         

**Harmonization status**:  complete  
**Harmonization comment**:   Specific study items's category: don't know/ no answer, is categorized as 3 | Neither agree or disagree that they feel lonely 
**R script**:  
```{r, echo=TRUE}

#this is what my supervisors said to do, categorize don't know as the neutral , please change as you see fit

table(CoP4_Baseline$ENV_FLLNLY_MCQ, useNA="always") 

soc_CLSA_cop_0$env_nbh_lone_0 <- ifelse(CoP4_Baseline$ENV_FLLNLY_MCQ ==1,1L, 
                                           ifelse(CoP4_Baseline$ENV_FLLNLY_MCQ==2,2L,
                                          ifelse(CoP4_Baseline$ENV_FLLNLY_MCQ==3,4L,
                                      ifelse(CoP4_Baseline$ENV_FLLNLY_MCQ==4,5L,
                                  ifelse(CoP4_Baseline$ENV_FLLNLY_MCQ==8,3L,NA)))))

table(soc_CLSA_cop_0$env_nbh_lone_0, useNA="always") 
```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_1      
**Variable description**: Indicator of whether the participant agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that they feel lonely   
2 | Agree that they feel lonely
3 | Neither agree or disagree that they feel lonely 
4 | Disagree that they feel lonely  
5 | Strongly disagree that they feel lonely         

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(CoP_FU1$ENV_FLLNLY_COF1, useNA="always") 

soc_CLSA_cop_1$env_nbh_lone_1 <- ifelse(CoP_FU1$ENV_FLLNLY_COF1 ==1,1L, 
                                           ifelse(CoP_FU1$ENV_FLLNLY_COF1==2,2L,
                                          ifelse(CoP_FU1$ENV_FLLNLY_COF1==3,4L,
                                      ifelse(CoP_FU1$ENV_FLLNLY_COF1==4,5L,
                                  ifelse(CoP_FU1$ENV_FLLNLY_COF1==8,3L,NA)))))

table(soc_CLSA_cop_1$env_nbh_lone_1, useNA="always") 
```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_2      
**Variable description**: Indicator of whether the participant agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that they feel lonely   
2 | Agree that they feel lonely
3 | Neither agree or disagree that they feel lonely 
4 | Disagree that they feel lonely 
5 | Strongly disagree that they feel lonely         

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_3      
**Variable description**: Indicator of whether the participant agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that they feel lonely   
2 | Agree that they feel lonely
3 | Neither agree or disagree that they feel lonely  
4 | Disagree that they feel lonely   
5 | Strongly disagree that they feel lonely        

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Lonely in neighbourhood        
**Variable name**: env_nbh_lone_4      
**Variable description**: Indicator of whether the participant agrees that they feel lonely in the area where they live (i.e. their community, their neighbourhood).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strongly agree that they feel lonely   
2 | Agree that they feel lonely
3 | Neither agree or disagree that they feel lonely 
4 | Disagree that they feel lonely  
5 | Strongly disagree that they feel lonely         

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Close-knit community        
**Variable name**: env_nbh_comm_0      
**Variable description**: Community in which participant lives is close-knit (i.e. neighbourhood solidarity).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strong neighbourhood solidarity     
2 | Some neighbourhood solidarity    
3 | A little neighbourhood solidarity    
4 | No neighbourhood solidarity                   

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 
### **Variable label**: Close-knit community        
**Variable name**: env_nbh_comm_1      
**Variable description**: Indicator of whether the participant agrees that members of the area in which participant lives are close-knit (community solidarity).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strong neighbourhood solidarity     
2 | Some neighbourhood solidarity    
3 | A little neighbourhood solidarity    
4 | No neighbourhood solidarity                   

**Harmonization status**:   impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Close-knit community        
**Variable name**: env_nbh_comm_2      
**Variable description**: Indicator of whether the participant agrees that members of the area in which participant lives are close-knit (community solidarity).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strong neighbourhood solidarity     
2 | Some neighbourhood solidarity    
3 | A little neighbourhood solidarity    
4 | No neighbourhood solidarity                   

**Harmonization status**:   impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Close-knit community        
**Variable name**: env_nbh_comm_3      
**Variable description**: Indicator of whether the participant agrees that members of the area in which participant lives are close-knit (community solidarity).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strong neighbourhood solidarity     
2 | Some neighbourhood solidarity    
3 | A little neighbourhood solidarity    
4 | No neighbourhood solidarity                   

**Harmonization status**:   impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Close-knit community        
**Variable name**: env_nbh_comm_4      
**Variable description**: Indicator of whether the participant agrees that members of the area in which participant lives are close-knit (community solidarity).    
**Value type**: integer      
**Variable unit**: N/A       
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Strong neighbourhood solidarity     
2 | Some neighbourhood solidarity    
3 | A little neighbourhood solidarity    
4 | No neighbourhood solidarity                   

**Harmonization status**:   impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```

# Neighbourhood aesthetics subdomain

### **Variable label**: Neighbourhood cleanliness   
**Variable name**:  env_nbh_clean_0  
**Variable description**:  Indicator of the participant's perception of the cleanliness (presence of rubbish) of the area where the respondent lives (i.e. their neighbourhood).      
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Area not very clean     
2 | Area not clean   
3 | Area mostly clean   
4 | Area clean             

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(CoP4_Baseline$ENV_CLEAN_MCQ) 

soc_CLSA_cop_0$env_nbh_clean_0 <- ifelse(CoP4_Baseline$ENV_CLEAN_MCQ ==1,4L, 
                                           ifelse(CoP4_Baseline$ENV_CLEAN_MCQ==2,3L,
                                            ifelse(CoP4_Baseline$ENV_CLEAN_MCQ==3,2L,
                                                   ifelse(CoP4_Baseline$ENV_CLEAN_MCQ==4,1L,NA))))

table(soc_CLSA_cop_0$env_nbh_clean_0) 
```
### **Variable label**: Neighbourhood cleanliness   
**Variable name**:  env_nbh_clean_1  
**Variable description**:  Indicator of the participant's perception of the cleanliness (presence of rubbish) of the area where the respondent lives (i.e. their neighbourhood).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Area not very clean     
2 | Area not clean   
3 | Area mostly clean   
4 | Area clean             

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(CoP_FU1$ENV_CLEAN_COF1, useNA="always") 

soc_CLSA_cop_1$env_nbh_clean_1 <- ifelse(CoP_FU1$ENV_CLEAN_COF1 ==1,4L, 
                                           ifelse(CoP_FU1$ENV_CLEAN_COF1==2,3L,
                                            ifelse(CoP_FU1$ENV_CLEAN_COF1==3,2L,
                                                   ifelse(CoP_FU1$ENV_CLEAN_COF1==4,1L,NA))))

table(soc_CLSA_cop_1$env_nbh_clean_1, useNA="always") 
```
### **Variable label**: Neighbourhood cleanliness dichotomized     
**Variable name**:  env_nbh_clean_dich_0  
**Variable description**:  Indicator of whether the participant perception of the cleanliness (presence of rubbish) of the area where respondent lives (i.e. their neighbourhood).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Area not clean  
1 | Area clean             


**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(CoP4_Baseline$ENV_CLEAN_MCQ, useNA="always") 

soc_CLSA_cop_0$env_nbh_clean_0 <- ifelse(CoP4_Baseline$ENV_CLEAN_MCQ ==1 | CoP4_Baseline$ENV_CLEAN_MCQ==2,1L, 
                                            ifelse(CoP4_Baseline$ENV_CLEAN_MCQ==3 | CoP4_Baseline$ENV_CLEAN_MCQ==4,0L,NA))

table(soc_CLSA_cop_0$env_nbh_clean_0, useNA="always") 
```
### **Variable label**: Neighbourhood cleanliness dichotomized     
**Variable name**:  env_nbh_clean_dich_1    
**Variable description**:  Indicator of whether the participant perception of the cleanliness (presence of rubbish) of the area where respondent lives (i.e. their neighbourhood).  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Area not clean 
1 | Area clean             
 

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(CoP_FU1$ENV_CLEAN_COF1, useNA="always") 

soc_CLSA_cop_1$env_nbh_clean_1 <- ifelse(CoP_FU1$ENV_CLEAN_COF1 ==1 | CoP_FU1$ENV_CLEAN_COF1==2,1L, 
                                            ifelse(CoP_FU1$ENV_CLEAN_COF1==3 | CoP_FU1$ENV_CLEAN_COF1==4,0L,NA))

table(soc_CLSA_cop_1$env_nbh_clean_1, useNA="always") 
```
### **Variable label**: Neighbourhood cleanliness dichotomized     
**Variable name**:  env_nbh_clean_dich_2    
**Variable description**:  Indicator of whether the participant perception of the cleanliness (presence of rubbish) of the area where respondent lives (i.e. their neighbourhood).    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Area not clean 
1 | Area clean             
 

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Neighbourhood noisiness (4-level)       
**Variable name**:  env_nbh_noise_0  
**Variable description**:  Indicator of whether the participant’s perception of presence of excessive noise in their neighbourhood.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Definitely excessive noise      
2 | Some excessive noise    
3 | A little excessive noise    
4 | No excessive noise            

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Neighbourhood noisiness (4-level)       
**Variable name**:  env_nbh_noise_1  
**Variable description**:  Indicator of whether the participant’s perception of presence of excessive noise in their neighbourhood.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Definitely excessive noise      
2 | Some excessive noise    
3 | A little excessive noise    
4 | No excessive noise            

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood noisiness (2-level)       
**Variable name**:  env_nbh_noise_dich_0    
**Variable description**:  Respondent’s perception of noise in their neighbourhood.          
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Noisy 
1 | Not noisy         
       

**Harmonization status**:  complete  
**Harmonization comment**: Study specific item asks about noise problems in current home, use with caution.    
**R script**:  
```{r, echo=TRUE}
table(CoP4_Baseline$ENV_HMPRB_NOI_MCQ, useNA="always") 

soc_CLSA_cop_0$env_nbh_noise_dich_0 <- ifelse(CoP4_Baseline$ENV_HMPRB_NOI_MCQ ==1,0L, 
                                            ifelse(CoP4_Baseline$ENV_HMPRB_NOI_MCQ==0,1L,NA))

table(soc_CLSA_cop_0$env_nbh_noise_dich_0, useNA="always") 
```
### **Variable label**: Neighbourhood noisiness (2-level)     
**Variable name**:  env_nbh_noise_dich_1  
**Variable description**:  Respondent’s perception of noise in their neighbourhood.            
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Noisy  
1 | Not noisy         
      

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(CoP_FU1$ENV_HMPRB_NOI_COF1, useNA="always") 

soc_CLSA_cop_1$env_nbh_noise_dich_1 <- ifelse(CoP_FU1$ENV_HMPRB_NOI_COF1 ==1,0L, 
                                            ifelse(CoP_FU1$ENV_HMPRB_NOI_COF1==0,1L,NA))

table(soc_CLSA_cop_1$env_nbh_noise_dich_1, useNA="always") 
```
### **Variable label**: Neighbourhood traffic noise        
**Variable name**:  env_nbh_traf_noise_0    
**Variable description**:  Indicator of  the participant's perception of presence of noise from traffic, in their neighbourhood.           
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
------------- | -------------  
0 | Traffic noise 
1 | No traffic noise         


**Harmonization status**:  impossible
**Harmonization comment**: 
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Neighbourhood traffic noise      
**Variable name**:  env_nbh_traf_noise_1  
**Variable description**:  Indicator of  the participant's perception of presence of noise from traffic, in their neighbourhood.            
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
------------- | -------------  
0 | Traffic noise 
1 | No traffic noise          


**Harmonization status**:  impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}


```
# Crime and vandalism subdomain

### **Variable label**: Neighbourhood violence  
**Variable name**: env_nbh_violence_0     
**Variable description**:  Indicator of the participant's perception of violence in their neighbourhood.  
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Violence in neighbourhood  
1 | No violence in neighbourhood
   

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood violence  
**Variable name**: env_nbh_violence_1     
**Variable description**: Indicator of the participant's perception of violence in their neighbourhood.       
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Violence in neighbourhood
1 | No violence in neighbourhood
     

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood violence  
**Variable name**: env_nbh_violence_2     
**Variable description**: Indicator of the participant's perception of violence in their neighbourhood.      
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Violence in neighbourhood  
1 | No violence in neighbourhood
   

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood antisocial and aggressive behaviour 
**Variable name**: env_nbs_anti_0  
**Variable description**: Indicator of the participant's perception of antisocial and aggressive behaviour in their neighbourhood.    
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Antisocial and aggressive behavior in neighbourhood 
1 | No antisocial and aggressive behavior in neighbourhood
     

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood antisocial and aggressive behaviour 
**Variable name**: env_nbs_anti_1  
**Variable description**: Indicator of the participant's perception of antisocial and aggressive behaviour in their neighbourhood.   
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Antisocial and aggressive behavior in neighbourhood 
1 | No antisocial and aggressive behavior in neighbourhood
     

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood antisocial and aggressive behaviour 
**Variable name**: env_nbs_anti_2  
**Variable description**: Indicator of the participant's perception of antisocial and aggressive behaviour in their neighbourhood.    
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Antisocial and aggressive behavior in neighbourhood  
1 | No antisocial and aggressive behavior in neighbourhood
    

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Neighbourhood graffiti and vandalism  
**Variable name**:  env_nbh_gv_0  
**Variable description**:  Indicator of the participant's perception of graffiti and/or vandalism in the area where the respondent lives (i.e. their neighbourhood).    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | No graffiti and/or vandalism 
1 | Graffiti and/or vandalism  
             

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(CoP4_Baseline$ENV_VNDLSM_MCQ, useNA="always") 

soc_CLSA_cop_0$env_nbh_gv_0 <- ifelse(CoP4_Baseline$ENV_VNDLSM_MCQ ==1 | CoP4_Baseline$ENV_VNDLSM_MCQ==2,1L, 
                                            ifelse(CoP4_Baseline$ENV_VNDLSM_MCQ==3 | CoP4_Baseline$ENV_VNDLSM_MCQ==4,0L,NA))

table(soc_CLSA_cop_0$env_nbh_gv_0, useNA="always") 
```
### **Variable label**: Neighbourhood graffiti and vandalism  
**Variable name**:  env_nbh_gv_1    
**Variable description**:  Indicator of the participant's perception of graffiti and/or vandalism in the area where the respondent lives (i.e. their neighbourhood).   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | No graffiti and/or vandalism 
1 | Graffiti and/or vandalism  
             

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(CoP_FU1$ENV_VNDLSM_COF1, useNA="always") 

soc_CLSA_cop_1$env_nbh_gv_1 <- ifelse(CoP_FU1$ENV_VNDLSM_COF1 ==1 | CoP_FU1$ENV_VNDLSM_COF1==2,1L, 
                                            ifelse(CoP_FU1$ENV_VNDLSM_COF1==3 | CoP_FU1$ENV_VNDLSM_COF1==4,0L,NA))

table(soc_CLSA_cop_1$env_nbh_gv_1, useNA="always") 
```
### **Variable label**: Neighbourhood graffiti and vandalism    
**Variable name**:  env_nbh_gv_2  
**Variable description**:  Indicator of the participant's perception of graffiti and/or vandalism in the area where the respondent lives (i.e. their neighbourhood).   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Graffiti and/or vandalism 
1 | No graffiti and/or vandalism   
           

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**: Theft of transportation method   
**Variable name**: env_nbh_theft_0     
**Variable description**:  Indicator of the participant's perception of the occurrence of theft of transport vehicle in their neighbourhood.  
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Theft of vehicle in neighbourhood  
1 | No theft of vehicle in neighbourhood


**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Theft of transportation method   
**Variable name**: env_nbh_theft_1     
**Variable description**: Indicator of the participant's perception of the occurrence of theft of transport vehicle in their neighbourhood.         
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
------------- | -------------  
0 | Theft of vehicle in neighbourhood  
1 | No theft of vehicle in neighbourhood


**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
### **Variable label**: Theft of transportation method   
**Variable name**: env_nbh_theft_2     
**Variable description**: Indicator of the participant's perception of the occurrence of theft of transport vehicle in their neighbourhood.        
**Value type**: integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Theft of vehicle in neighbourhood  
1 | No theft of vehicle in neighbourhood


**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```
